---
title: "EM5_2_analysis"
format: html
editor: visual
---

# Preregistered plan

Hypotheses will be tested using Generalized Linear Mixed-Effect Models (Lo & Andrews, 2015) with *Condition* as a fixed effect and child (*participant*) as a random intercept, and with appropriate linking functions.

The model for Study Time will have an inverse Gaussian linking function because of its similar distribution to reaction times (Lo & Andrews, 2015).

The model for Memory Usage will have an identity linking function because based on the results of our previous studies, we expect it to follow a normal distribution. If there are substantive violations of the assumptions of these analyses, we will corroborate results with analogous non-parametric tests.

### Load libraries and data

```{r load libs n data}
# Load libraries & general setup
library(tidyverse)
library(ggpubr)
library(ggforce)
library(effectsize)
library(lme4)
library(lmerTest)
library(emmeans)
library(MuMIn)
library(MCMCglmm)
library(mixedpower)
library(DHARMa)

# Disable scientific notation
options(scipen = 999)

# Set working directory
setwd("D:/Canna_d/EM5_stuff/EM5_April_2025")

# Read in file
data <- read.csv("Summarized_first_trips_April25.csv", header = TRUE)

# label closing trial
data$condsFile <- ifelse(data$trial == 4, 
                       paste0(data$condsFile, "Closing"), 
                       data$condsFile)

# Read in file for age and combine with data
ages <- read.csv("ages.csv", header = T)
data <- left_join(data, ages, by = "participant")

# Make output more interpretable
options(contrasts = c("contr.sum","contr.poly"))

```

## Study time

### Process data

```{r process study time data}
# Average over all trials for each condition, for each child, as per preregistration
summarized_data <- data %>%
  group_by(participant, condsFile) %>%
  summarize(mean_MU = mean(meanMU, na.rm = TRUE),
            mean_StudyTime = mean(meanListTime, na.rm = TRUE),
            mean_Streak = mean(meanCorBefInc, na.rm = TRUE),
            age = first(Age),
            .groups = 'drop')

# Make sure condition is a factor
summarized_data$condsFile <- as.factor(summarized_data$condsFile)

# Remove closing trials for the free-response only analyses
freeResponseOnly <- summarized_data %>%
  filter(!(condsFile %in% c("noDelayClosing", "longDelayClosing")))
```

### Model study time

```{r study time model}
# Run the model
studyTimeGlmm <- glmer(mean_StudyTime ~ condsFile + (1|participant), 
                         data = freeResponseOnly, 
                         family = inverse.gaussian(link = "identity"))

# Below goes through diagnostic plots and checks
plot(density(freeResponseOnly$mean_StudyTime), 
     xlim=c(0, 160), ylim=c(0, 1), main='M_1 y_hat')
lines(density(predict(studyTimeGlmm, type='response')), col='red')

plot(studyTimeGlmm)

residuals <- residuals(studyTimeGlmm)
qqnorm(residuals)
qqline(residuals, col = "red")

library(performance)
check_model(studyTimeGlmm)


# Below we will compare the full model with the null model
mixConTime_GLMM_null <- glmer(mean_StudyTime ~ 1 + (1|participant), 
                              data = freeResponseOnly, 
                              family = inverse.gaussian(link = "identity"))
mixTimeConAov <- cbind(car::Anova(studyTimeGlmm),
                       r.squaredGLMM(studyTimeGlmm,mixConTime_GLMM_null)) 

# Compare the models
anova(mixConTime_GLMM_null,studyTimeGlmm)

# Get summary
summary(studyTimeGlmm)
mixTimeConAov

# Pairwise comparisons
contrasts(freeResponseOnly$condsFile)
emmeans(studyTimeGlmm, pairwise ~ condsFile)
```

#### Age effects model & KS test

To check the distribution of age and to (exploratory) see if age has an effect on any DV's.

```{r study time age effects}
# Run the KS test
ks.test(freeResponseOnly$age, "punif", 
        min(freeResponseOnly$age), 
        max(freeResponseOnly$age))

# Plot the density of actual data
plot(density(freeResponseOnly$age), 
     main = "Age Distribution vs Uniform", 
     xlab = "Age", 
     ylab = "Density", 
     xlim = c(min(freeResponseOnly$age), max(freeResponseOnly$age)),
     lwd = 2)

# Add a horizontal line for the uniform distribution's density
abline(h = 1 / (max(freeResponseOnly$age) - min(freeResponseOnly$age)), 
       col = "red", lty = 2, lwd = 2)

legend("topright", legend = c("Observed Density", "Uniform Density"),
       col = c("black", "red"), lty = c(1,2), lwd = 2)

# Center age
freeResponseOnly$age.ct <- freeResponseOnly$age - mean(freeResponseOnly$age)

# Run the age model for study time
studyTimeGlmmAge <- glmer(mean_StudyTime ~ condsFile + 
                         + age.ct + age.ct*condsFile + (1|participant), 
                         data = freeResponseOnly, 
                         family = inverse.gaussian(link = "identity"))

# Diagnostics
plot(density(freeResponseOnly$mean_StudyTime), 
     xlim=c(0, 160), ylim=c(0, 1), main='M_1 y_hat')
lines(density(predict(studyTimeGlmmAge, type='response')), col='red')

plot(studyTimeGlmmAge)

residuals <- residuals(studyTimeGlmmAge)
qqnorm(residuals)
qqline(residuals, col = "red")

library(performance)
check_model(studyTimeGlmmAge)

# Full VS null model
mixConTime_GLMM_null <- glmer(mean_StudyTime ~ 1 + (1|participant), 
                              data = freeResponseOnly, 
                              family = inverse.gaussian(link = "identity"))
mixTimeConAov <- cbind(car::Anova(studyTimeGlmmAge),
                       r.squaredGLMM(studyTimeGlmmAge,mixConTime_GLMM_null)) 

# Compare the models
anova(mixConTime_GLMM_null,studyTimeGlmmAge)

# get summary
summary(studyTimeGlmmAge)
mixTimeConAov
```

## Memory Usage

```{r model for MU}
# View the distribution of MU
hist(freeResponseOnly$mean_MU)

# Run the model
MU_GLMM <- glmer(mean_MU ~ condsFile + (1|participant),
                 data = freeResponseOnly, 
                    family = gaussian(link = "identity"))

# Below runs diagnostic plots and checks
plot(density(freeResponseOnly$mean_MU), xlim=c(-50, 50), ylim=c(0, 0.6), 
     main='M_1 y_hat')
lines(density(predict(MU_GLMM, type='response') ), col='red')

plot(MU_GLMM)

residuals <- residuals(MU_GLMM)
qqnorm(residuals)
qqline(residuals, col = "red")

check_model(MU_GLMM)

# Compare the full vs the null model
MUfree_null <- glmer(mean_MU ~ 1 + (1|participant), 
                     data = freeResponseOnly, family = gaussian(link = "identity"))
MUfreeAov <- cbind(car::Anova(MU_GLMM),
                   r.squaredGLMM(MU_GLMM,MUfree_null))

anova(MUfree_null,MU_GLMM)

# Get summary
summary(MU_GLMM)
MUfreeAov

# pairwise comparisons
emmeans(MU_GLMM, pairwise ~ condsFile)
```

#### Age effects model

```{r MU age effects}

# Run the model for age effects with MU
MU_GLMMAge <- glmer(mean_MU ~ condsFile + 
                   + age.ct + age.ct*condsFile + (1|participant),
                 data = freeResponseOnly, family = gaussian(link = "identity"))

# Diagnostics
plot(density(freeResponseOnly$mean_MU), xlim=c(-50, 50), ylim=c(0, 0.6), 
     main='M_1 y_hat')
lines(density(predict(MU_GLMMAge, type='response') ), col='red')

plot(MU_GLMMAge)

residuals <- residuals(MU_GLMMAge)
qqnorm(residuals)
qqline(residuals, col = "red")

check_model(MU_GLMMAge)

# Compare full model with null model
MUfree_null <- glmer(mean_MU ~ 1 + (1|participant), 
                     data = freeResponseOnly, family = gaussian(link = "identity"))
MUfreeAov <- cbind(car::Anova(MU_GLMMAge),
                   r.squaredGLMM(MU_GLMMAge,MUfree_null))

anova(MUfree_null,MU_GLMMAge)

# get summary
summary(MU_GLMMAge)
MUfreeAov
```

## Free VS Total response

### Process data

```{r process free v total}
library(dplyr)
# Label cond-type to say if its free or total-response
summarized_data <- summarized_data %>%
  mutate(condType = case_when(
    condsFile %in% c("noDelayClosing", "longDelayClosing") ~ "Total",
    condsFile %in% c("noDelay", "longDelay") ~ "Free",
    TRUE ~ NA_character_
  ))

# Average over participant and condition
freeVtotal <- summarized_data %>%
  group_by(participant, condType) %>%
  summarize(mean_MU = mean(mean_MU, na.rm = TRUE),
            mean_StudyTime = mean(mean_StudyTime, na.rm = TRUE),
            age = first(age),
            .groups = 'drop')
```

### Model free V total

```{r free v total model}
# Observe distribution
hist(freeVtotal$mean_MU)

# Run the model
freeVtotal_glmm <- glmer(mean_MU ~ condType + (1|participant),
                 data = freeVtotal, 
                    family = gaussian(link = "identity"))

# Run diagnostic plots and checks
plot(density(freeVtotal$mean_MU), xlim=c(-50, 50), ylim=c(0, 0.6), 
     main='M_1 y_hat')
lines(density(predict(freeVtotal_glmm, type='response') ), col='red')

plot(freeVtotal_glmm)

residuals <- residuals(freeVtotal_glmm)
qqnorm(residuals)
qqline(residuals, col = "red")

check_model(freeVtotal_glmm)

# Compare full with null model
MUfree_null <- glmer(mean_MU ~ 1 + (1|participant), 
                     data = freeVtotal, family = gaussian(link = "identity"))
MUfreeAov <- cbind(car::Anova(freeVtotal_glmm),
                   r.squaredGLMM(freeVtotal_glmm,MUfree_null))

anova(MUfree_null,freeVtotal_glmm)

# Check summary
summary(freeVtotal_glmm)
MUfreeAov
```

#### Age effects model Free V Total

```{r free v total age model}
# Center age
freeVtotal$age.ct <- freeVtotal$age - mean(freeVtotal$age)

# Run the model
freeVtotal_glmmAge <- glmer(mean_MU ~ condType + + age.ct + age.ct*condType
                         + (1|participant), data = freeVtotal, 
                    family = gaussian(link = "identity"))

# Diagnostics
plot(density(freeVtotal$mean_MU), xlim=c(-50, 50), ylim=c(0, 0.6), 
     main='M_1 y_hat')
lines(density(predict(freeVtotal_glmmAge, type='response') ), col='red')

plot(freeVtotal_glmmAge)

residuals <- residuals(freeVtotal_glmmAge)
qqnorm(residuals)
qqline(residuals, col = "red")

check_model(freeVtotal_glmmAge)

# Full VS null model
MUfree_null <- glmer(mean_MU ~ 1 + (1|participant), 
                     data = freeVtotal, family = gaussian(link = "identity"))
MUfreeAov <- cbind(car::Anova(freeVtotal_glmmAge),
                   r.squaredGLMM(freeVtotal_glmmAge,MUfree_null))

anova(MUfree_null,freeVtotal_glmmAge)

# Check summary
summary(freeVtotal_glmmAge)
MUfreeAov
```

## Exploratory analyses

Wilcoxon paired t-tests

```{r t test exploratory}
# Rename values in the 'condsFile' column
freeResponseOnly$condsFile <- as.character(freeResponseOnly$condsFile)
freeResponseOnly$condsFile[freeResponseOnly$condsFile == "No-Delay"] <- "noDelay"
freeResponseOnly$condsFile[freeResponseOnly$condsFile == "Long-Delay"] <- "longDelay"

# MU
# Restructure data into wide format
wide_data <- freeResponseOnly %>%
  select(participant, condsFile, mean_MU) %>%
  pivot_wider(names_from = condsFile, values_from = mean_MU)

# Run the test
wilcox.test(wide_data$noDelay, wide_data$longDelay, paired = TRUE, alternative = "two.sided")

# Study time
# Restructure data into wide format
wide_data_ST <- freeResponseOnly %>%
  select(participant, condsFile, mean_StudyTime) %>%
  pivot_wider(names_from = condsFile, values_from = mean_StudyTime)

# Run the test
wilcox.test(wide_data_ST$noDelay, wide_data_ST$longDelay, paired = TRUE, alternative = "two.sided")

# Free V Total
# Restructure data into wide format
wide_data_FvT <- freeVtotal %>%
  select(participant, condType, mean_MU) %>%
  pivot_wider(names_from = condType, values_from = mean_MU)

# Run the test
wilcox.test(wide_data_FvT$Free, wide_data_FvT$Total, paired = TRUE, alternative = "two.sided")

```

### Metacognition questions

```{r metacog}
# Set working directory
setwd("D:/Canna_d/EM5_stuff/EM5_April_2025")

# Read in data
metacog <- read.csv("metacog_EM52.csv",header=TRUE)

# Only get participants who were included in analyses
metacog_d <- metacog[metacog$Participant %in% freeResponseOnly$participant, ]

# Get tables for kids responses
# Q: Which game did you think was harder?
metaSum <- cbind(harder= table(metacog_d$Harder_clean)) %>% data.frame()
# Q: When the store was closing, did the game get harder?
metaSumClosing <- cbind(Closing= table(metacog_d$Closing_harder_clean)) %>% data.frame()
# Q: When the store was closing, did you feel like you were guessing or not?
metaSumGuess <- cbind(Guess = table(metacog_d$Guess_clean)) %>% data.frame()

# Run binomial tests on answers
harderTest <- binom.test(metaSum$harder[2],sum(metaSum$harder),0.5)
closingTest <- binom.test(metaSumClosing$Closing[2],sum(metaSumClosing$Closing),0.5)
guessTest <- binom.test(metaSumGuess$Guess[2],sum(metaSumGuess$Guess),0.5)
```

### Order effects

Have to do preprocessing again:

```{r order effects process}
# Average over all trials for each condition, for each child, as per preregistration
summarized_data <- data %>%
  group_by(participant, condsFile, order) %>%
  summarize(mean_MU = mean(meanMU, na.rm = TRUE),
            mean_StudyTime = mean(meanListTime, na.rm = TRUE),
            mean_Streak = mean(meanCorBefInc, na.rm = TRUE),
            age = first(Age),
            .groups = 'drop')

# make sure condition and order is a factor
summarized_data$condsFile <- as.factor(summarized_data$condsFile)
summarized_data$order <- as.factor(summarized_data$order)

# Remove closing trials
freeResponseOnly <- summarized_data %>%
  filter(!(condsFile %in% c("noDelayClosing", "longDelayClosing")))
```

#### Order effects: study time

```{r order study time}
# Run model
studyTimeOrder <- glmer(mean_StudyTime ~ condsFile + order + (1|participant), 
                         data = freeResponseOnly, 
                         family = inverse.gaussian(link = "identity"))
# Check summary
summary(studyTimeOrder)
# Visualize
plot(freeResponseOnly$order, freeResponseOnly$mean_StudyTime)
```

#### Order effects: MU

```{r order mu}
# Run model
MU_order <- glmer(mean_MU ~ condsFile + order + (1|participant),
                 data = freeResponseOnly, 
                    family = gaussian(link = "identity"))
# Check summary
summary(MU_order)
# Compare null with full
MUOrder_null <- glmer(mean_MU ~ 1 + (1|participant), 
                     data = freeResponseOnly, family = gaussian(link = "identity"))

MUfreeAov <- cbind(car::Anova(MU_order),
                   r.squaredGLMM(MU_order,MUOrder_null))
# Visualize
plot(freeResponseOnly$order, freeResponseOnly$mean_MU)
# Check p values
MUfreeAov
```

### Block effects

Whether or not performance decreases over time.

```{r trial effects}
# Make sure trial is a factor
data$trial <- as.factor(data$trial)

# Order B, no delay first
orderB <- data[data$order == "B",]

# Only look at free-response trials
orderB <- orderB %>%
  filter(!(condsFile %in% c("noDelayClosing", "longDelayClosing")))

ggplot(orderB, aes(x = factor(trial), y = meanListTime)) +
  geom_boxplot() +
  facet_wrap(~ condsFile) +
  labs(x = "Trial", y = "Study Time", title = "Study Time by Trial and Condition, order B") +
  theme_minimal()

ggplot(orderB, aes(x = factor(trial), y = meanMU)) +
  geom_boxplot() +
  facet_wrap(~ condsFile) +
  labs(x = "Trial", y = "MU", title = "MU by Trial and Condition, order B") +
  theme_minimal()

# Order D, long delay first
orderD <- data[data$order == "D",]

# Only look at free-response trials
orderD <- orderD %>%
  filter(!(condsFile %in% c("noDelayClosing", "longDelayClosing")))

ggplot(orderD, aes(x = factor(trial), y = meanListTime)) +
  geom_boxplot() +
  facet_wrap(~ condsFile) +
  labs(x = "Trial", y = "Study Time", title = "Study Time by Trial and Condition, order D") +
  theme_minimal()

ggplot(orderD, aes(x = factor(trial), y = meanMU)) +
  geom_boxplot() +
  facet_wrap(~ condsFile) +
  labs(x = "Trial", y = "MU", title = "MU by Trial and Condition, order D") +
  theme_minimal()
```

#### Block effects model

```{r block effects models}
# Remove closing trials
data_noClosing <- data %>%
  filter(!(condsFile %in% c("noDelayClosing", "longDelayClosing")))

# Run model for study time
studyTime_block <- glmer(meanListTime ~ condsFile + trial + (1|participant), 
                         data = data_noClosing, 
                         family = inverse.gaussian(link = "identity"))
# Check summary
summary(studyTime_block)

## MU
# Run model for MU
MU_block <- glmer(meanMU ~ condsFile + trial + (1|participant),
                 data = data_noClosing, 
                    family = gaussian(link = "identity"))
# Check summary
summary(MU_block)
# Compare null with full
MU_null <- glmer(meanMU ~ 1 + (1|participant), 
                     data = data_noClosing, family = gaussian(link = "identity"))

MUfreeAov <- cbind(car::Anova(MU_block),
                   r.squaredGLMM(MU_block,MU_null))
# Check p values
MUfreeAov
```

### No-delay Total VS Long-delay Total

```{r nd total vs ld total}
# Only look at Closing trials
totalResponseOnly <- summarized_data %>%
  filter((condsFile %in% c("noDelayClosing", "longDelayClosing")))

# Look at distirbution
hist(totalResponseOnly$mean_MU)

# Run model
MUtotal_GLMM <- glmer(mean_MU ~ condsFile + (1|participant),
                 data = totalResponseOnly, 
                    family = gaussian(link = "identity"))

# Diagnostic plots
plot(density(totalResponseOnly$mean_MU), xlim=c(-50, 50), ylim=c(0, 0.6), 
     main='M_1 y_hat')
lines(density(predict(MUtotal_GLMM, type='response') ), col='red')

plot(MUtotal_GLMM)

residuals <- residuals(MUtotal_GLMM)
qqnorm(residuals)
qqline(residuals, col = "red")

check_model(MUtotal_GLMM)

# Check full VS null
MUfree_null <- glmer(mean_MU ~ 1 + (1|participant), 
                     data = totalResponseOnly, family = gaussian(link = "identity"))
MUfreeAov <- cbind(car::Anova(MUtotal_GLMM),
                   r.squaredGLMM(MUtotal_GLMM,MUfree_null))

anova(MUfree_null,MUtotal_GLMM)

# Check summary
summary(MUtotal_GLMM)
MUfreeAov
```

## Effect size

It can be difficult and/or problematic to compute effect size for mixed models perhaps, but here it goes.

```{r effect sizes}

## Eta squared
library(effectsize)
model <- lmer(mean_StudyTime ~ condsFile + (1 | participant), data = freeResponseOnly)
eta_squared(model)

model <- lmer(mean_MU  ~ condsFile + (1 | participant), data = freeResponseOnly)
eta_squared(model)

model <- lmer(mean_MU  ~ condType  + (1 | participant), data = freeVtotal)
eta_squared(model)
```

### Screen use

```{r screen use}
# Group by participant
participant_data <- data %>%
  group_by(participant) %>%
  slice(1) %>%
    ungroup()

# Organize into numeric data
participant_data <- participant_data %>%
  mutate(screen_use_numeric = case_when(
    On.these.days..how.many.hours.does.your.child.typically.spend.using.the.touchscreen.device. == "0" ~ 0,
    On.these.days..how.many.hours.does.your.child.typically.spend.using.the.touchscreen.device. == "0-1 hour" ~ 1,
    On.these.days..how.many.hours.does.your.child.typically.spend.using.the.touchscreen.device. == "1-2 hours" ~ 2,
    On.these.days..how.many.hours.does.your.child.typically.spend.using.the.touchscreen.device. == "2-3 hours" ~ 3,
    TRUE ~ NA_real_
  ))

# Get mean and SD
mean(participant_data$screen_use_numeric, na.rm = T)
sd(participant_data$screen_use_numeric, na.rm = T)
```

### All trips

```{r all trips process data}
# Read in file
data <- read.csv("Summarized_data_April25.csv", header = TRUE)

# label closing trial
data$condsFile <- ifelse(data$trial == 4, 
                       paste0(data$condsFile, "Closing"), 
                       data$condsFile)

# Read in file for age and combine with data
ages <- read.csv("ages.csv", header = T)
data <- left_join(data, ages, by = "participant")
```

#### Study time

```{r all trips study time}
# Average over all trials for each condition, for each child, as per preregistration
summarized_data <- data %>%
  group_by(participant, condsFile) %>%
  summarize(mean_MU = mean(meanMU, na.rm = TRUE),
            mean_StudyTime = mean(meanListTime, na.rm = TRUE),
            mean_Streak = mean(meanCorBefInc, na.rm = TRUE),
            age = first(Age),
            .groups = 'drop')

# make sure condition is a factor
summarized_data$condsFile <- as.factor(summarized_data$condsFile)

# Remove closing trials
freeResponseOnly_all <- summarized_data %>%
  filter(!(condsFile %in% c("noDelayClosing", "longDelayClosing")))

# Run the model
studyTime_all <- glmer(mean_StudyTime ~ condsFile + (1|participant), 
                         data = freeResponseOnly_all, 
                         family = inverse.gaussian(link = "identity"))

# Full VS null
mixConTime_GLMM_null <- glmer(mean_StudyTime ~ 1 + (1|participant), 
                              data = freeResponseOnly_all, 
                              family = inverse.gaussian(link = "identity"))

mixTimeConAov <- cbind(car::Anova(studyTime_all),
                       r.squaredGLMM(studyTime_all,mixConTime_GLMM_null)) 

# Effect size
library(effectsize)
model <- lmer(mean_StudyTime ~ condsFile + (1|participant), 
                         data = freeResponseOnly_all)
eta_squared(model)
```

#### MU

```{r all trips mu}
# Run the model
MU_GLMM <- glmer(mean_MU ~ condsFile + (1|participant),
                 data = freeResponseOnly_all, 
                    family = gaussian(link = "identity"))

# Full VS null
MUfree_null <- glmer(mean_MU ~ 1 + (1|participant), 
                     data = freeResponseOnly_all, family = gaussian(link = "identity"))
MUfreeAov <- cbind(car::Anova(MU_GLMM),
                   r.squaredGLMM(MU_GLMM,MUfree_null))

# Effect size
model <- lmer(mean_MU ~ condsFile + (1|participant), 
                         data = freeResponseOnly_all)
eta_squared(model)
```

### Comparisons with Liang et al.

Trips

```{r trips}
# Read in file
all_trips <- read.csv("Summarized_data_April25.csv", header = TRUE)

# Get mean and SD
mean(all_trips$nTrip[all_trips$condsFile == "noDelay"],)
mean(all_trips$nTrip[all_trips$condsFile == "longDelay"],)
sd(all_trips$nTrip[all_trips$condsFile == "noDelay"],)
sd(all_trips$nTrip[all_trips$condsFile == "longDelay"],)
```

Streak correct

```{r streak}
# Get mean and SD
mean(freeResponseOnly$mean_Streak[freeResponseOnly$condsFile == "noDelay"],)
mean(freeResponseOnly$mean_Streak[freeResponseOnly$condsFile == "longDelay"],)
sd(freeResponseOnly$mean_Streak[freeResponseOnly$condsFile == "noDelay"],)
sd(freeResponseOnly$mean_Streak[freeResponseOnly$condsFile == "longDelay"],)
```
