---
title: "EM5_1_analysis"
format: html
editor: visual
---

## Preregistered plan

Unless specified otherwise, hypotheses will be tested using Generalized Linear Mixed-Effect Models (Lo & Andrews, 2015) with Condition and Age as fixed effects and participant as a random effect, and with appropriate linking functions. If there are substantive violations of the assumptions of these analyses, we will corroborate results with non-parametric tests.

## Process data

```{r process data}
# Load libraries & general setup
library(tidyverse)
library(ggpubr)
library(ggforce)
library(effectsize)
library(lme4)
library(lmerTest)
library(emmeans)
library(MuMIn)
library(MCMCglmm)
library(mixedpower)
library(DHARMa)

# Disable scientific notation
options(scipen = 999)

# Set the correct working directory
#setwd("D:/Canna_d/EM5_stuff/EM5_data/Indivivual_participant_data/placeholder")

# Load file
multiDataTrialSum <- read.csv("multiDataTrialSum1Trip.csv", header = TRUE)

# Remove the old One-shot
no1shot <- multiDataTrialSum %>%
  filter(!condsFile == "oneShot3.2") %>%
  filter(!condsFile == "oneShotClosing")

# Rename Closing trials as Total-response
data <- no1shot %>%
  mutate(condsFile = case_when(
    condsFile %in% c("noDelayClosing", "longDelayClosing") ~ "totalResponse",
    TRUE ~ condsFile  # Keep the original value for all other cases
  ))

# Make output more interpretable
options(contrasts = c("contr.sum","contr.poly"))
```

## Study time

```{r study time model}
# Average over all trials for each condition, for each child, as per preregistration
study_time <- data %>%
  group_by(participant, condsFile) %>%
  summarize(mean_MU = mean(meanMU, na.rm = TRUE),
            mean_StudyTime = mean(meanListTime, na.rm = TRUE), 
            age = first(age), 
            .groups = 'drop')

# Center age
study_time$age.ct <- study_time$age - mean(study_time$age)

# make sure condition is a factor
study_time$condsFile <- as.factor(study_time$condsFile)

# Run model
studyTimeGlmm <- glmer(mean_StudyTime ~ condsFile + age.ct + age.ct*condsFile + (1|participant), 
                         data = study_time, 
                         family = inverse.gaussian(link = "identity"), nAGQ = 0)

# Below runs model diagnostic plots and tests
plot(density(study_time$mean_StudyTime), xlim=c(0, 160), ylim=c(0, 1), main='M_1 y_hat')
lines(density(predict(studyTimeGlmm, type='response')), col='red')

plot(studyTimeGlmm)

residuals <- residuals(studyTimeGlmm)
qqnorm(residuals)
qqline(residuals, col = "red")

# Below we will compare model with one that has no fixed effects
# To see if the fixed effects (condsFile) is important at explaining the data
mixConTime_GLMM_null <- glmer(mean_StudyTime ~ 1 + (1|participant), 
                              data = study_time, 
                              family = inverse.gaussian(link = "identity"), nAGQ = 0)
mixTimeConAov <- cbind(car::Anova(studyTimeGlmm),
                       r.squaredGLMM(studyTimeGlmm,mixConTime_GLMM_null)) 

# Compare the models
anova(mixConTime_GLMM_null,studyTimeGlmm)

# Look at the summary
summary(studyTimeGlmm)
mixTimeConAov

# Pairwise comparisons
contrasts(study_time$condsFile)
emmeans(studyTimeGlmm, pairwise ~ condsFile)
```

## Memory Use

```{r mu model}
# Average over participant and condition
MU_data <- data %>%
  group_by(participant, condsFile) %>%
  summarize(mean_MU = mean(meanMU, na.rm = TRUE), 
            age = first(age), 
            .groups = 'drop')

# Center age
MU_data$age.ct <- MU_data$age - mean(MU_data$age)

# Run the model
MU_GLMM <- glmer(mean_MU ~ condsFile + age.ct + age.ct*condsFile + (1|participant), 
                    data = MU_data, 
                    family = gaussian(link = "identity"))

# Below runs model diagnostic plots and tests
plot(density(MU_data$mean_MU), xlim=c(-50, 50), ylim=c(0, 0.6), main='M_1 y_hat')
lines(density(predict(MU_GLMM, type='response') ), col='red')

plot(MU_GLMM)

residuals <- residuals(MU_GLMM)
qqnorm(residuals)
qqline(residuals, col = "red")

# Summary
summary(MU_GLMM)

# Get the p value, and R squared
MUfree_null <- glmer(mean_MU ~ 1 + (1|participant), 
                     data = MU_data, family = gaussian(link = "identity"))
MUfreeAov <- cbind(car::Anova(MU_GLMM),
                   r.squaredGLMM(MU_GLMM,MUfree_null))

# Comparing if the full fits better than the null model
anova(MUfree_null,MU_GLMM)

# Pairwise comparisons
library(emmeans)
emmeans(MU_GLMM, list(pairwise ~ condsFile), adjust = "tukey")

```

### MU Free VS Total

```{r hypotheses 3 and 4}
# Make sure dplyr is loaded
library(dplyr)

# Set cond-type to say whether it was Free-response or Total-response
condType_data <- no1shot %>%
  mutate(condType = case_when(
    condsFile %in% c("noDelayClosing", "longDelayClosing") ~ "Total",
    condsFile %in% c("noDelay", "longDelay") ~ "Free",
    TRUE ~ NA_character_
  ))

# Average over participant and condition
freeVtotal <- condType_data %>%
  group_by(participant, condType) %>%
  summarize(mean_MU = mean(meanMU, na.rm = TRUE),
            mean_StudyTime = mean(meanListTime, na.rm = TRUE),
            age = first(age),
            .groups = 'drop')

# Look at distribution of data
hist(freeVtotal$mean_MU)

# Model
freeVtotal_glmm <- glmer(mean_MU ~ condType + (1|participant),
                 data = freeVtotal, 
                    family = gaussian(link = "identity"))

# Below runs model diagnostic plots and tests
plot(density(freeVtotal$mean_MU), xlim=c(-50, 50), ylim=c(0, 0.6), 
     main='M_1 y_hat')
lines(density(predict(freeVtotal_glmm, type='response') ), col='red')

plot(freeVtotal_glmm)

residuals <- residuals(freeVtotal_glmm)
qqnorm(residuals)
qqline(residuals, col = "red")

# Use check_model from performance
library(performance)
check_model(freeVtotal_glmm)

# Compare full model with null model
MUfree_null <- glmer(mean_MU ~ 1 + (1|participant), 
                     data = freeVtotal, family = gaussian(link = "identity"))
MUfreeAov <- cbind(car::Anova(freeVtotal_glmm),
                   r.squaredGLMM(freeVtotal_glmm,MUfree_null))

anova(MUfree_null,freeVtotal_glmm)

# Get the summary
summary(freeVtotal_glmm)
MUfreeAov
```

### Effect size

```{r effect sizes}

# Get eta squared
library(effectsize)
model <- lmer(mean_StudyTime ~ age.ct * condsFile + (1 | participant), data = study_time)
eta_squared(model)

model_mu <- lmer(mean_MU ~ age.ct * condsFile + (1 | participant), data = MU_data)
eta_squared(model_mu)
```

### KS Test

This test is to see how distributed our ages are.

```{r ks test}
# Run the KS test
ks.test(MU_data$age, "punif", 
        min(MU_data$age), 
        max(MU_data$age))

# Plot the density of actual data
plot(density(MU_data$age), 
     main = "Age Distribution vs Uniform", 
     xlab = "Age", 
     ylab = "Density", 
     xlim = c(min(MU_data$age), max(MU_data$age)),
     ylim = c(0,0.6),
     lwd = 2)

# Add a horizontal line for the uniform distribution's density
abline(h = 1 / (max(MU_data$age) - min(MU_data$age)), 
       col = "red", lty = 2, lwd = 2)

legend("topright", legend = c("Observed Density", "Uniform Density"),
       col = c("black", "red"), lty = c(1,2), lwd = 2)
```

### Order effects

```{r order effects process}
# Average over all trials for each condition, for each child, as per preregistration
summarized_data <- data %>%
  group_by(participant, condsFile, order) %>%
  summarize(mean_MU = mean(meanMU, na.rm = TRUE),
            mean_StudyTime = mean(meanListTime, na.rm = TRUE),
            mean_Streak = mean(meanCorBefInc, na.rm = TRUE),
            age = first(age),
            .groups = 'drop')

# make sure condition and order is a factor
summarized_data$condsFile <- as.factor(summarized_data$condsFile)
summarized_data$order <- as.factor(summarized_data$order)

# Center age
summarized_data$age.ct <- summarized_data$age - mean(summarized_data$age)

```

#### Order effects: study time

```{r order study time}
# Run the model
studyTimeOrder <- glmer(mean_StudyTime ~ condsFile + order + 
                          age.ct + age.ct*condsFile + (1|participant), 
                         data = summarized_data, 
                         family = inverse.gaussian(link = "identity"))

# Check summary
summary(studyTimeOrder)

# Visualize
plot(summarized_data$order, summarized_data$mean_StudyTime)
```

#### Order effects: MU

```{r order MU}
# Run the model
MU_order <- glmer(mean_MU ~ condsFile + order + 
                    age.ct + age.ct*condsFile + (1|participant),
                 data = summarized_data, 
                    family = gaussian(link = "identity"))

# Check summary
summary(MU_order)

# Compare null with full
MUOrder_null <- glmer(mean_MU ~ 1 + (1|participant), 
                     data = summarized_data, family = gaussian(link = "identity"))

MUfreeAov <- cbind(car::Anova(MU_order),
                   r.squaredGLMM(MU_order,MUOrder_null))

# Visualize
plot(summarized_data$order, summarized_data$mean_MU)

# Check p value
MUfreeAov
```

### Block effects

Whether or not performance decreases over time.

```{r block effects}
# Make sure trialis a factor
data$trial <- as.factor(data$trial)

# Order B, no delay first
orderB <- data[data$order == "B",]

orderB <- orderB %>%
  filter(!(condsFile %in% c("totalResponse")))

ggplot(orderB, aes(x = factor(trial), y = meanListTime)) +
  geom_boxplot() +
  facet_wrap(~ condsFile) +
  labs(x = "Trial", y = "Study Time", title = "Study Time by Trial and Condition, order B") +
  theme_minimal()

ggplot(orderB, aes(x = factor(trial), y = meanMU)) +
  geom_boxplot() +
  facet_wrap(~ condsFile) +
  labs(x = "Trial", y = "MU", title = "MU by Trial and Condition, order B") +
  theme_minimal()

# Order D, long delay first
orderD <- data[data$order == "D",]

orderD <- orderD %>%
  filter(!(condsFile %in% c("totalResponse")))

ggplot(orderD, aes(x = factor(trial), y = meanListTime)) +
  geom_boxplot() +
  facet_wrap(~ condsFile) +
  labs(x = "Trial", y = "Study Time", title = "Study Time by Trial and Condition, order D") +
  theme_minimal()

ggplot(orderD, aes(x = factor(trial), y = meanMU)) +
  geom_boxplot() +
  facet_wrap(~ condsFile) +
  labs(x = "Trial", y = "MU", title = "MU by Trial and Condition, order D") +
  theme_minimal()
```

## Supplementary materials

### Old One-shot info

```{r old one shot}
# Rename Closing trials as Total-response
multiDataTrialSum <- multiDataTrialSum %>%
  mutate(condsFile = case_when(
    condsFile %in% c("noDelayClosing", "longDelayClosing") ~ "One_Shot",
    TRUE ~ condsFile  # Keep the original value for all other cases
  ))

# Needs to be a factor to rename
multiDataTrialSum$condsFile <- as.factor(multiDataTrialSum$condsFile)

# Rename
levels(multiDataTrialSum$condsFile)[levels(multiDataTrialSum$condsFile) == "oneShot3.2"] <- "Old_One_Shot"
levels(multiDataTrialSum$condsFile)[levels(multiDataTrialSum$condsFile) == "oneShotClosing"] <- "Old_One_Shot_closing"

# MU
# Group by participant and conditions
MU_suppMaterials <- multiDataTrialSum %>%
     group_by(participant, condsFile) %>%
     summarize(mean_MU = mean(meanMU, na.rm = TRUE),
               age = first(age),
               .groups = 'drop')

# Get table of summary stats
MU_suppMaterials %>%
  group_by(condsFile) %>%
  summarise(
    Mean = mean(mean_MU, na.rm = TRUE),
    SD = sd(mean_MU, na.rm = TRUE),
    Min = min(mean_MU, na.rm = TRUE),
    Max = max(mean_MU, na.rm = TRUE),
    age = first(age),
    .groups = "drop"
  )

# Study time
# Group by participant and condition
ST_suppMaterials <- multiDataTrialSum %>%
     group_by(participant, condsFile) %>%
     summarize(mean_ST = mean(meanListTime, na.rm = TRUE), 
               age = first(age),
               .groups = 'drop')

# Get table of summary stats
ST_suppMaterials %>%
  group_by(condsFile) %>%
  summarise(
    Mean = mean(mean_ST, na.rm = TRUE),
    SD = sd(mean_ST, na.rm = TRUE),
    Min = min(mean_ST, na.rm = TRUE),
    Max = max(mean_ST, na.rm = TRUE),
    .groups = "drop"
  )

# Remove total-response trials
noTR <- MU_suppMaterials %>%
  filter(!condsFile == "Old_One_Shot_closing") %>%
  filter(!condsFile == "One_Shot")

# Center age
noTR$age.ct <- noTR$age - mean(noTR$age)

# Model for MU
MU_Old_oneShot <- glmer(mean_MU ~ condsFile + + age.ct + age.ct*condsFile +
                          (1|participant), 
                    data = noTR, 
                    family = gaussian(link = "identity"))

summary(MU_Old_oneShot)
MU_null <- glmer(mean_MU ~ 1 + (1|participant), 
                     data = noTR, family = gaussian(link = "identity"))
MUAov <- cbind(car::Anova(MU_Old_oneShot),
                   r.squaredGLMM(MU_Old_oneShot,MU_null))

# Effect size MU
library(effectsize)
model <- lmer(mean_MU  ~ condsFile + (1 | participant), data = noTR)
eta_squared(model)

model <- lmer(mean_MU  ~ age.ct + (1 | participant), data = noTR)
eta_squared(model)

model <- lmer(mean_MU  ~ age.ct*condsFile + (1 | participant), data = noTR)
eta_squared(model)

# Model for Study time
# Remove total-response trials
noTR_ST <- ST_suppMaterials %>%
  filter(!condsFile == "Old_One_Shot_closing") %>%
  filter(!condsFile == "One_Shot")

noTR_ST$age.ct <- noTR_ST$age - mean(noTR_ST$age)

ST_Old_oneShot <- glmer(mean_ST ~ condsFile + age.ct + age.ct*condsFile + 
                          (1|participant), 
                         data = noTR_ST, 
                         family = inverse.gaussian(link = "identity"), nAGQ = 0)

summary(ST_Old_oneShot)
ST_null <- lmer(mean_ST ~ 1 + (1|participant), 
                     data = noTR_ST)
STAov <- cbind(car::Anova(ST_Old_oneShot),
                   r.squaredGLMM(ST_Old_oneShot,ST_null))

# Effect sizes
model <- lmer(mean_ST  ~ condsFile + (1 | participant), data = noTR_ST)
eta_squared(model)

model <- lmer(mean_ST  ~ age.ct + (1 | participant), data = noTR_ST)
eta_squared(model)

model <- lmer(mean_ST  ~ age.ct*condsFile + (1 | participant), data = noTR_ST)
eta_squared(model)

## Free VS Total response
# Set cond-type to say whether it was Free-response or Total-response
condType_data_supp <- multiDataTrialSum %>%
  mutate(condType = case_when(
    condsFile %in% c("One_Shot", "Old_One_Shot_closing") ~ "Total",
    condsFile %in% c("noDelay", "longDelay", "Old_One_Shot") ~ "Free",
    TRUE ~ NA_character_
  ))

# Average over participant and condition
freeVtotal_supp <- condType_data_supp %>%
  group_by(participant, condType) %>%
  summarize(mean_MU = mean(meanMU, na.rm = TRUE),
            mean_StudyTime = mean(meanListTime, na.rm = TRUE),
            age = first(age),
            .groups = 'drop')

# Model
freeVtotal_glm_supp <- glmer(mean_MU ~ condType + (1|participant),
                 data = freeVtotal_supp, 
                    family = gaussian(link = "identity"))

MUsupp_null <- glmer(mean_MU ~ 1 + (1|participant), 
                     data = freeVtotal_supp, family = gaussian(link = "identity"))
MUfreeAov <- cbind(car::Anova(freeVtotal_glm_supp),
                   r.squaredGLMM(freeVtotal_glm_supp,MUsupp_null))

# Effect size
model <- lmer(mean_MU  ~ condType + (1 | participant), data = freeVtotal_supp)
eta_squared(model)

# Model
freeVtotal_st_supp <- lmer(mean_StudyTime ~ condType + (1|participant),
                 data = freeVtotal_supp)

STsupp_null <- lmer(mean_StudyTime ~ 1 + (1|participant), 
                     data = freeVtotal_supp)
STAov <- cbind(car::Anova(freeVtotal_st_supp),
                   r.squaredGLMM(freeVtotal_st_supp,STsupp_null))

```

#### Screen use

```{r screen use}

# Group by participant 
participant_data <- data %>%
  group_by(participant) %>%
  slice(1) %>%
    ungroup()

# Organize into numeric data
participant_data <- participant_data %>%
  mutate(screen_use_numeric = case_when(
    screen_use_hour == "0" ~ 0,
    screen_use_hour == "0-1 hour" ~ 1,
    screen_use_hour == "1-2 hours" ~ 2,
    screen_use_hour == "2-3 hours" ~ 3,
    TRUE ~ NA_real_
  ))

# Get mean and SD
mean(participant_data$screen_use_numeric, na.rm = T)
sd(participant_data$screen_use_numeric, na.rm = T)

```

#### All trips

```{r all trips process}
# Set the correct working directory (only when running locally)
setwd("D:/Canna_d/EM5_stuff/EM5_data/Indivivual_participant_data/placeholder")

# Load file
multiDataTrialSum <- read.csv("multiDataTrialSum.csv", header = TRUE)

# Remove the old One-shot
no1shot <- multiDataTrialSum %>%
  filter(!condsFile == "oneShot3.2") %>%
  filter(!condsFile == "oneShotClosing")

# Rename Closing trials as Total-response
data <- no1shot %>%
  mutate(condsFile = case_when(
    condsFile %in% c("noDelayClosing", "longDelayClosing") ~ "totalResponse",
    TRUE ~ condsFile  # Keep the original value for all other cases
  ))
```

##### Study time

```{r all trips study time}
# Average over all trials for each condition, for each child, as per preregistration
study_time <- data %>%
  group_by(participant, condsFile) %>%
  summarize(mean_MU = mean(meanMU, na.rm = TRUE),
            mean_StudyTime = mean(meanListTime, na.rm = TRUE), 
            age = first(age), 
            .groups = 'drop')

# Center age
study_time$age.ct <- study_time$age - mean(study_time$age)

# make sure condition is a factor
study_time$condsFile <- as.factor(study_time$condsFile)

# Run model
studyTime_all <- glmer(mean_StudyTime ~ condsFile + age.ct + age.ct*condsFile + (1|participant), 
                         data = study_time, 
                         family = inverse.gaussian(link = "identity"), nAGQ = 0)

mixConTime_GLMM_null <- glmer(mean_StudyTime ~ 1 + (1|participant), 
                              data = study_time, 
                              family = inverse.gaussian(link = "identity"), nAGQ = 0)
mixTimeConAov <- cbind(car::Anova(studyTime_all),
                       r.squaredGLMM(studyTime_all,mixConTime_GLMM_null)) 

# Effect size
library(effectsize)
model <- lmer(mean_StudyTime ~ condsFile + (1|participant), 
                         data = study_time)
eta_squared(model)

model <- lmer(mean_StudyTime ~ age.ct + (1|participant), 
                         data = study_time)
eta_squared(model)

model <- lmer(mean_StudyTime ~ age.ct*condsFile + (1|participant), 
                         data = study_time)
eta_squared(model)
```

##### MU

```{r all trips mu}
# Average over participant and condition
MU_data <- data %>%
  group_by(participant, condsFile) %>%
  summarize(mean_MU = mean(meanMU, na.rm = TRUE), 
            age = first(age), 
            .groups = 'drop')

# Center age
MU_data$age.ct <- MU_data$age - mean(MU_data$age)

# Run the model
MU_all <- glmer(mean_MU ~ condsFile + age.ct + age.ct*condsFile + (1|participant), 
                    data = MU_data, 
                    family = gaussian(link = "identity"))

# Get the p value, and R squared
MUfree_null <- glmer(mean_MU ~ 1 + (1|participant), 
                     data = MU_data, family = gaussian(link = "identity"))
MUfreeAov <- cbind(car::Anova(MU_all),
                   r.squaredGLMM(MU_all,MUfree_null))

# Effect size
model <- lmer(mean_MU ~ condsFile + (1|participant), 
                         data = MU_data)
eta_squared(model)

model <- lmer(mean_MU ~ age.ct + (1|participant), 
                         data = MU_data)
eta_squared(model)

model <- lmer(mean_MU ~ age.ct*condsFile + (1|participant), 
                         data = MU_data)
eta_squared(model)
```

### Comparisons with Liang et al.

Trips

```{r trips}
# Set the correct working directory (only when running locally)
setwd("D:/Canna_d/EM5_stuff/EM5_data/Indivivual_participant_data/placeholder")

# Load file
multiDataTrialSum <- read.csv("multiDataTrialSum.csv", header = TRUE)

# Get mean and SD
mean(multiDataTrialSum$nTrip[multiDataTrialSum$condsFile == "noDelay"],)
mean(multiDataTrialSum$nTrip[multiDataTrialSum$condsFile == "longDelay"],)
sd(multiDataTrialSum$nTrip[multiDataTrialSum$condsFile == "noDelay"],)
sd(multiDataTrialSum$nTrip[multiDataTrialSum$condsFile == "longDelay"],)
```

Streak correct

```{r streak correct}
# Average over participant and condition
Streak_data <- data %>%
  group_by(participant, condsFile) %>%
  summarize(mean_Streak = mean(meanCorBefInc, na.rm = TRUE), 
            .groups = 'drop')

# Get mean and SD
mean(Streak_data$mean_Streak[Streak_data$condsFile == "noDelay"],)
mean(Streak_data$mean_Streak[Streak_data$condsFile == "longDelay"],)
sd(Streak_data$mean_Streak[Streak_data$condsFile == "noDelay"],)
sd(Streak_data$mean_Streak[Streak_data$condsFile == "longDelay"],)

```
