---
title: "EM5_2_preprocessing"
format: html
editor: visual
---

## Prep

### Load libraries + initialize

```{r load libs etc}
# Set working directory
#setwd("D:/Canna_d/EM5_stuff/EM5_April_2025/raw_data")

# Load libraries
library(lme4)
library(lmerTest)
library(emmeans)
library(effectsize)
library(tidyverse)
library(ggpubr)

# Initialize data frames
allFiles <- list.files(pattern=".csv$")
all_Real_Data <- data.frame()
all_Clicked <- data.frame()
all_Correct_Clicked <- data.frame()

# If I ever used the escape key to end the exp instead of pressing "q",
# these columns don't get written to the dataframe,
# So here we remove them as we don't need them for analysis anyway
columns_to_remove <- c("goRightMouse.clicked_name", "endExp.keys",
                       "endExp.rt","endExp.started", "endExp.stopped",
                       "expFeedbackText.started","expFeedbackText.stopped")
```

### Extract data files

Keep in mind these differences between EM5 and EM5_2:

-   EM5_2 has two conditions: no-delay and long-delay

-   EM5_2 has a binary column in the csv to indicate closing, called "closing"

```{r extract data}
# Set working directory
#setwd("D:/Canna_d/EM5_stuff/EM5_April_2025/raw_data")

# Extract data files
for (d in 1:length(allFiles)){
  all_Data <- read.csv(allFiles[d],header=TRUE,fileEncoding="UTF-8-BOM")
  all_Data <- all_Data[, !(colnames(all_Data) %in% columns_to_remove)]
  # Remove .csv extension for readability
  all_Data$condsFile <- all_Data$condsFile %>% str_replace(".csv","") 
  # Filter out the practice trials
  real_Data <- all_Data %>% filter(realOrNot == 1) %>% 
    # Filter out the introduction and instruction screens
    filter(condsFile!="mixed") %>% 
    filter(trialFeedBackPress.keys!="q") %>% 
    # Select the relevant columns
    select("participant","condsFile","delayDuration","order",
           "multipleTrials.thisN","oneTrial.thisN","templateTime"
           ,"templateFrame","nCorrect","nIncorrect",
           "clickedImages","clickedImagesTime",
           "correctClickedsName","correctClickedsTime",
           "correctImages","curCorrectImages",
           "workingTime","workingFrame", "closing") %>%
    # Rename for readability
    rename(trial = multipleTrials.thisN, trip = oneTrial.thisN,
           listTime = templateTime, listFrame = templateFrame ,
           shelfTime = workingTime, shelfFrame = workingFrame,
           remainCorAfterTrip = curCorrectImages,
           numCorrect = nCorrect,
           numIncorrect = nIncorrect)
  # Increment trip and trial index by 1 because the starting point is 0
  real_Data$trial <- real_Data$trial+1  
  real_Data$trip <- real_Data$trip+1
  # Initialize columns containing the number of correct/incorrect for the current trip
  real_Data[,c("nCurCorrect","nCurIncorrect","nCurClickeds")] <- NA 
  
  # Create new data frames that will hold the number of correct clicks per participant
  curParClicked <- data.frame()
  curParCorrectClicked <- data.frame()
  # Create dataframe called "current_Info" that holds the information about the current moment in the for-loop
  for (n in 1:nrow(real_Data)){
    
    current_Info <- real_Data[n, c("participant","condsFile","delayDuration","order", 
                             "trial","trip","listTime","listFrame","numCorrect",
                             "numIncorrect","shelfTime",'shelfFrame',
                             "correctImages", "closing")] # added closing 4/12
    # Clean the values in the column that specifies how many correct selections are left
    # Note that when we use str_split(), the values turn into a list, so to keep it in vector form we use unlist()
    # length() gets the count, so this variable will be a count of the number of correct selections that are left
    curCorRemain <- real_Data$remainCorAfterTrip[n] %>%  gsub("\\[|\\]","",.) %>% 
      gsub(" ","",.) %>% gsub("\'","",.) %>% str_split(",") %>% unlist() %>%   
      length() 
    # Clean the values from having weird characters
    # setNames changes the name of the column
    # First, we look at all of the attempts
    curClickedName <- real_Data$clickedImages[n] %>%  gsub("\\[|\\]","",.) %>% 
      gsub(" ","",.) %>% gsub("\'","",.) %>% str_split(",") %>% 
      setNames("clickName")
    curClickedTime <-real_Data$clickedImagesTime[n] %>% gsub("\\[|\\]","",.) %>%
      str_split(",") %>% unlist %>% as.numeric() %>% list() %>% 
      setNames("clickTime")
    # Combine the info with the names of what was clicked and the time
    curClicked <- cbind(current_Info,curClickedName,row.names=NULL) %>% 
      cbind(curClickedTime,row.names=NULL)
    # Now, we are cleaning the values for the correct attempts
    curCorClickedName <- real_Data$correctClickedsName[n] %>%  
      gsub("\\[|\\]","",.) %>% gsub(" ","",.) %>% gsub("\'","",.) %>% 
      str_split(",") %>% setNames("corClickName") 
    curCorClickedTime <-real_Data$correctClickedsTime[n] %>% 
      gsub("\\[|\\]","",.) %>% str_split(",") %>% unlist %>% as.numeric() %>% 
      list() %>% setNames("corClickTime")
    # Combine the info with the names and the times of what was clicked
    curCorClicked <-  cbind(current_Info,curCorClickedName,row.names=NULL) %>% 
      cbind(curCorClickedTime, row.names=NULL)
    # set nCurCorrect to be a count of what was correctly clicked, and nCurClickeds to be a count of what was attempted
    real_Data[n,c("nCurCorrect","nCurClickeds")] <- 
      c(length(na.omit(curCorClickedTime$corClickTime)),
        length(na.omit(curClickedTime$clickTime))) 
    # A new column, nRemainCorrect, gets the number of the remaining correct items added to the count of correct clicks
    real_Data[n,"nRemainCorrect"] <- 
      curCorRemain+length(na.omit(curCorClickedTime$corClickTime))
    # Information about what a participant clicked goes in curParClicked, and info about what they clicked correctly goes in curParCorrectClicked
    curParClicked <- rbind(curParClicked, curClicked)
    curParCorrectClicked <- rbind(curParCorrectClicked, curCorClicked)
  }
  
  # Set incorrect clicks to be the number of clicks minus the number of correct clicks
  real_Data$nCurIncorrect <- real_Data$nCurClickeds-real_Data$nCurCorrect 
  # Add the current iteration's data to the mother dataset, all_Real_Data
  all_Real_Data <- rbind(all_Real_Data,real_Data)
  all_Clicked <- rbind(all_Clicked,curParClicked) 
  all_Correct_Clicked <- rbind(all_Correct_Clicked,curParCorrectClicked)  
  
}
```

### Checkpoint - save csv

```{r checkpoint 1}
write.csv(all_Real_Data,"all_Real_Data_check1_April2025.csv",row.names = FALSE)
write.csv(all_Clicked,"all_Clicked_check1_April2025.csv",row.names = FALSE) 
write.csv(all_Correct_Clicked,"all_Cor_Clicked_check1_April2025.csv",row.names = FALSE) 
```

## Process performance

### Calculating correct responses

```{r getting correct taps}
# Make a dataframe containing the participant names and one containing the names of the conditions
participants <- unique(all_Clicked$participant)
cond <- unique(all_Clicked$condsFile)
# Initialize a data frame that will hold the information about each trip
newAllclicked <- data.frame()
# Add columns to the dataframe that contains all of the clicked data that will contain information about performance
all_Clicked[,c("clickAccuracy","remainCorImage","nRemainCor", 
              "remainOptions")] <- NA

# This for-loop will iterate over each participant and calculate their performance
for (p in 1:length(participants)){
  # In the for-loop, we are going to look at one participant at a time
  curParClicked <- all_Clicked %>% filter(participant==participants[p]) 
  # And we are going to look at one condition at a time
  for (c in 1: length(cond)){
    curCond <- curParClicked %>% filter(condsFile == cond[c])
    # Set trials to be the unique values in the "trial" column for this condition
    trials <- unique(curCond$trial)
    # Now we are going to look at one trial at a time
    for (t in 1:length(trials)){
      curTrial <- curCond %>% filter(trial == trials[t])
      # Clean the first value in the correctImages column for readability
      curCorrectIm <- curTrial$correctImages[1] %>%  gsub("\\[|\\]","",.) %>%
        gsub(" ","",.) %>% gsub("\'","",.) %>% str_split(",") %>% unlist()
      # Set trips to be the unique values in the "trip" column for this trial
      trips <- unique(curTrial$trip)
      # Now we are going to look at one trip at a time (within the trial, within the condition, within the participant)
      for (tr in 1:length(trips)){
        curTrip <- curTrial %>% filter(trip == trips[tr])
        if (nrow(curTrip) == 0) {
  warning(paste("Empty curTrip for participant", participants[p], 
                "condition", cond[c], 
                "trial", trials[t], 
                "trip", trips[tr]))
  next
}
        # The remaining options for any given trip, at the beginning, is always 10 (10 pairs of 2-AFC)
        nRemainOption <- 10
        # For each trip, make sure we know what images are currently correct
        for (q in 1: nrow(curTrip)){
          curTrip$remainCorImage[q] <- vapply(list(curCorrectIm),
                                              paste,collapse=",",character(1L))
          # nRemainCor is the count of how many correct options are left
          curTrip$nRemainCor[q] <- length(curCorrectIm)
          # remainOptions is how many clickable images are left
          curTrip$remainOptions[q] <- nRemainOption 
          # clickAccuracy is whether the clicked image is correct or not
          curTrip$clickAccuracy[q] <- 
            as.numeric(curTrip$clickName[q] %in% curCorrectIm)
          # Here, the remaining options become 10 minus the number of clicks you made
          nRemainOption <- nRemainOption -length(na.omit(curTrip$clickTime[q])) 
          # And the correct options that are left are the correct options not yet clicked on
          curCorrectIm <- curCorrectIm[!curCorrectIm %in% curTrip$clickName[q]] 
        }
        # newAllClicked will hold the information about each trip
        newAllclicked <- rbind(newAllclicked,curTrip)
      }
    }
  }
}
```

### Checkpoint 2, save csv

```{r checkpoint 2}
write.csv(newAllclicked,"all_Clicked_check2_April2025.csv",row.names = FALSE)

```

### Streak correct

```{r calc streak correct}
# Initialize the dataframe
allClickedBe4Incor <- data.frame()

for (p in 1:length(participants)){
  # In the for-loop, we are going to look at one participant at a time, one condition at a time, one trial and then one trip at a time
  curParClicked <- newAllclicked %>% filter(participant==participants[p])
  for (c in 1: length(cond)){
    curCond <- curParClicked %>% filter(condsFile == cond[c])
    trials <- unique(curCond$trial)
    for (t in 1:length(trials)){
      curTrial <- curCond %>% filter(trial == trials[t])
      trips <- unique(curTrial$trip)
      # Now we are we will go within the trip
      for (tr in 1:length(trips)){
        curTrip <- curTrial %>% filter(trip == trips[tr])
        # Here, correctIndex is assigned the first instance where the accuracy is zero, or the first instance where the participant was incorrect
        correctIndex <- (which(curTrip$clickAccuracy==0))[1]
        # if correctIndex is NA, it means that the participant did not click on anything, so their streak is not broken, so collect the data from this trip
        if (is.na(correctIndex)){
          validTripClick <- curTrip
          # if correctIndex is 1, we want this row to be in ValidTripClick
        } else if(correctIndex == 1) {
          validTripClick <- curTrip[1,] 
          # if correctIndex is indeed 0, make sure validTripClick contains the first row of the current trip up until (but not including) the first incorrect response
        } else{
          validTripClick <- curTrip[1:correctIndex-1,]
        }
        # Combine it into a dataframe
        allClickedBe4Incor <- rbind(allClickedBe4Incor,validTripClick) 
      }
      
    }
    
  }
}

# Get the sum of the streak correct for each trip
allClickedBe4IncorSum <- allClickedBe4Incor %>% 
  group_by(participant,condsFile,trial,trip) %>% 
  summarize(nCurCorBe4Inc = sum(clickAccuracy,na.rm = T)) %>% 
  ungroup()

# Combine with the mother dataset
all_Real_Data <- merge(all_Real_Data,allClickedBe4IncorSum) %>% 
  relocate(nCurCorBe4Inc,.after=nCurCorrect)

```

### Checkpoint, save csv

```{r checkpoint 3}
write.csv(all_Real_Data,"all_Real_Data_check3_April2025.csv",row.names = FALSE)

```

### MU Calculation

```{r get MU}
# Calculate Memory Usage
# MU = (((numCorrect/numAttempted)-0.5)/0.5)*numAttempted 
all_Real_Data <- all_Real_Data %>%
  group_by(participant, condsFile, trial, trip) %>%
  mutate(MU = (((nCurCorrect / nCurClickeds) - 0.5) / 0.5) * nCurClickeds)

# Replace NaNs with zeroes, because NaNs in MU occurred when the participant did not make any clicks (so they used zero memory)
all_Real_Data$MU[is.nan(all_Real_Data$MU)] <- 0
```

### Checkpoint, save csv

```{r checkpoint 4}
write.csv(all_Real_Data,"all_Real_Data_Mu_check4_April25.csv",row.names = FALSE)

```

## Outlier calculation

```{r outliers log study time}
# Now, let's check for outliers
# Note: we will be looking at the MAD
# Note: the list time is NOT normally distributed - it has a long tail to the right
# So we log transform it first
all_Real_Data$log_listTime <- log10(all_Real_Data$listTime)

# Make new dataset
exclusions <- all_Real_Data

# Filter by condition
longDelay <- exclusions %>% 
  filter(condsFile == "longDelay")

noDelay <- exclusions %>% 
  filter(condsFile == "noDelay")

# Below calculates MAD for the Long-delay condition
MAD_longDelay <- mad(longDelay$log_listTime)
# Calculate maximum and minimum thresholds
threshold_maximum <- median(longDelay$log_listTime, na.rm = TRUE) + (3*MAD_longDelay)
threshold_minimum <- median(longDelay$log_listTime, na.rm = TRUE) - (3*MAD_longDelay)
# Now determine which rows are outliers
outlier_rows_LD <- subset(longDelay, log_listTime > threshold_maximum)
outlier_rows_minimum_LD <- subset(longDelay, log_listTime < threshold_minimum)

# Same for each condition
MAD_noDelay <- mad(noDelay$log_listTime)
threshold_maximum <- median(noDelay$log_listTime, na.rm = TRUE) + (3*MAD_noDelay)
threshold_minimum <- median(noDelay$log_listTime, na.rm = TRUE) - (3*MAD_noDelay)
outlier_rows_ND <- subset(noDelay, log_listTime > threshold_maximum)
outlier_rows_minimum_ND <- subset(noDelay, log_listTime < threshold_minimum)

# Combine all outlier rows
outliers <- rbind(outlier_rows_LD, outlier_rows_minimum_LD,
                    outlier_rows_ND, outlier_rows_minimum_ND
                    )

# Make sure the variables are numeric
outliers$trial <- as.numeric(outliers$trial)
outliers$trip <- as.numeric(outliers$trip)
outliers$nCurCorBe4Inc <- as.numeric(outliers$nCurCorBe4Inc)
outliers$MU <- as.numeric(outliers$MU)

# Inspect each case of an excluded row to see if any excluded rows result in:
  # 1. No trips for a given trial (if so, exclude trial)
  # 2. Only 1/3 of free-response or no total-response? Remove condition for that participant

# Change participant number below as needed for inspection
inspect_exclusions <- all_Real_Data %>%
  filter(participant == 55)

# participant 55: participant excluded, outliers on both closing
# participant 5: long delay trial 3
# participant 23: long delay condition
# participant 28: long delay trial 3

# Remove outliers here
all_Real_Data_exclusions <- anti_join(all_Real_Data, outliers, by = c("participant", "condsFile", "trip", "trial"))

# Now we remove any participants or conditions that need to be excluded
all_Real_Data_exclusions <- all_Real_Data_exclusions %>%
  filter(!(participant == 55) & 
           !(condsFile == "longDelay" & trial == 3 & participant == "w005") &
           !(condsFile == "longDelay" & participant == "w023") &
           !(condsFile == "longDelay" & trial == 3 & participant == "w028")) 
         
# Visually inspect
inspect_exclusions <- all_Real_Data_exclusions %>%
  filter(participant == 55)

# Plot list time after exclusions
ggplot(data = all_Real_Data_exclusions,mapping = aes(x = listTime))+
  geom_histogram(binwidth = 1)+
  theme_pubr(base_size = 20, base_family ="serif")+
  theme(panel.spacing = unit(0, "lines"), 
        strip.background = element_blank(),
        #strip.placement = "inside",
        #axis.title.y = element_blank(),
        #axis.title.x = element_blank()
  )+
  scale_x_continuous(breaks=c(0,30,60,90))

ggplot(data = all_Real_Data,mapping = aes(x = listTime))+
  geom_histogram(binwidth = 1)+
  theme_pubr(base_size = 20, base_family ="serif")+
  theme(panel.spacing = unit(0, "lines"), 
        strip.background = element_blank(),
        #strip.placement = "inside",
        #axis.title.y = element_blank(),
        #axis.title.x = element_blank()
  )+
  scale_x_continuous(breaks=c(0,30,60,90))

# Exclusions are good, make it our working dataset
all_Real_Data_no_exclusions <- all_Real_Data
all_Real_Data <- all_Real_Data_exclusions

# Make sure there is a first trip for every trial
unique_combinations_no_trip_1 <- all_Real_Data %>%
  group_by(participant, condsFile, trial) %>%
  summarise(has_trip_1 = any(trip == 1), .groups = 'drop') %>%
  filter(!has_trip_1) %>%
  select(participant, condsFile, trial)
# Looks good! This code should output an empty dataset
```

### Checkpoint, save csv

```{r checkpoint 5}
write.csv(all_Real_Data,"all_Real_Data_AFTER_exclusions_April25.csv",row.names = FALSE)
```

## Demographics

```{r read in demo}
demo <- read.csv("raw_data/demographics_EM52.csv",header=TRUE)
demo$Participant.number <- as.factor(demo$Participant.number)
names(demo)[names(demo) == "Participant.number"] <- "participant"


# normalize participant column
all_Real_Data$participant <- gsub("^w0*", "", all_Real_Data$participant)
all_Real_Data$participant <- as.factor(all_Real_Data$participant)
```

## Summarizing data

```{r summariizing data}
Summarized_data <- all_Real_Data %>% 
  group_by(participant,condsFile,order,trial) %>% 
  summarise(nTrip=n(),
            totalListTime=sum(listTime,na.rm = T),
            meanListTime = mean(listTime,na.rm = T),
            totalShelfTime = sum(shelfTime,na.rm = T),
            meanShelfTime = mean(shelfTime,na.rm = T),
            totalTime = totalListTime + totalShelfTime,
            totalCorrect=sum(nCurCorrect),
            meanCorrect = totalCorrect/nTrip,
            meanCorBefInc=sum(nCurCorBe4Inc)/nTrip,
            totalInCorrect = sum(nCurIncorrect),
            meanIncorrect = totalInCorrect/nTrip,
            maxCorrect = max(nCurCorrect),
            maxIncorrect = max(nCurIncorrect),
            totalClickeds=sum(nCurClickeds),
            meanclickeds=totalClickeds/nTrip,
            meanMU = mean(MU, na.rm = TRUE)
  ) %>% left_join(demo, by = "participant")

write.csv(Summarized_data,"Summarized_data_April25.csv",row.names = FALSE)
         
# Do the same but for first trips only
first_trip_only <- all_Real_Data %>%
  filter(trip == 1)

Summarized_first_trips <- first_trip_only %>% 
  group_by(participant,condsFile,order,trial) %>% 
  summarise(nTrip=n(),
            totalListTime=sum(listTime,na.rm = T),
            meanListTime = mean(listTime,na.rm = T),
            totalShelfTime = sum(shelfTime,na.rm = T),
            meanShelfTime = mean(shelfTime,na.rm = T),
            totalTime = totalListTime + totalShelfTime, 
            totalCorrect=sum(nCurCorrect),
            meanCorrect = totalCorrect/nTrip,
            meanCorBefInc=sum(nCurCorBe4Inc)/nTrip,
            totalInCorrect = sum(nCurIncorrect),
            meanIncorrect = totalInCorrect/nTrip,
            maxCorrect = max(nCurCorrect),
            maxIncorrect = max(nCurIncorrect),
            totalClickeds=sum(nCurClickeds),
            meanclickeds=totalClickeds/nTrip,
            meanMU = mean(MU, na.rm = TRUE)
  ) %>% left_join(demo, by = "participant")

write.csv(Summarized_first_trips,"Summarized_first_trips_April25.csv",row.names = FALSE)
```
