---
title: "EM5_2_analysis"
format: html
editor: visual
---

## Manuscript title

How much do you remember when it’s up to you? Measuring memory use without response bias in young children

Last edited: 10/3/25

In this file there is the preregistered main analyses, secondary analyses, as well as the analyses and descriptive statistics used for the supplementary materials.

Variable and data descriptions:

| Experiment2_data.csv | ages.csv | metacog_exp2.csv | lastQ_everyone.csv | Experiment2_allTrips.csv |
|----|----|----|----|----|
| participant: participant ID | participant: participant ID | participant: participant ID | participant: participant ID | participant: participant ID |
| condsFile: condition | Age: rounded age | Harder_clean: child's response to which condition they thought was harder | Age: rounded age | condsFile: condition |
| order: counterbalanced order |  | Closing_harder_clean: child's response to whether they thought the total-response trials were harder than the free-response trials | How you played: children's responses to the final, open ended strategy question in Exp 2 | order: counterbalanced order |
| trial: trial number |  | Guess_clean: child's response to whether they felt they were guessing in the total-response trials |  | trial: trial number |
| nTrip: trip ID (always 1) |  |  |  | nTrip: trip ID |
| totalListTime: absolute time studying the list |  |  |  | totalListTime: absolute time studying the list |
| meanListTime: average time studying the list (same as totalListTime since this data is for first-trips only) |  |  |  | meanListTime: average time studying the list |
| totalShelfTime: absolute time selecting items in the store |  |  |  | totalShelfTime: absolute time selecting items in the store |
| meanShelfTime: average selecting items in the store (same as totalShelf Time since this data is for first-trips only) |  |  |  | meanShelfTime: average selecting items in the store |
| totalTime: absolute time in the first trip studying the list and selecting items in the store |  |  |  | totalTime: absolute time in the first trip studying the list and selecting items in the store |
| totalCorrect: sum of correct selections |  |  |  | totalCorrect: sum of correct selections |
| meanCorrect: mean of correct selections (same as totalCorrect since this data is for first-trips only) |  |  |  | meanCorrect: mean of correct selections |
| meanCorBefInc: mean correct selections before making an incorrect selection |  |  |  | meanCorBefInc: mean correct selections before making an incorrect selection |
| totalInCorrect: sum of incorrect selections |  |  |  | totalInCorrect: sum of incorrect selections |
| meanIncorrect: mean of incorrect selections (same as totalInCorrect since this data is for first-trips only) |  |  |  | meanIncorrect: mean of incorrect selections |
| maxCorrect: maximum amount of correct selections (same as totalCorrect since this data is for first-trips only) |  |  |  | maxCorrect: maximum amount of correct selections |
| maxIncorrect: maximum amount of incorrect selections (same as totalInCorrect since this data is for first-trips only) |  |  |  | maxIncorrect: maximum amount of incorrect selections |
| totalClickeds: sum of all selections made |  |  |  | totalClickeds: sum of all selections made |
| meanclickeds: mean of all selections made (same as totalClickeds since this data is for first-trips only) |  |  |  | meanclickeds: mean of all selections made |
| meanMU: average value of Memory Use |  |  |  | meanMU: average value of Memory Use |
| Timestamp: date and time of completion of demographic form |  |  |  | Timestamp: date and time of completion of demographic form |
| What.is.your.child.s.gender.: child's gender (parent reported) |  |  |  | What.is.your.child.s.gender.: child's gender (parent reported) |
| What.is.your.child.s.age.: child's age (parent reported) |  |  |  | What.is.your.child.s.age.: child's age (parent reported) |
| Please.enter.your.child.s.birth.date.: child's birthday (parent reported) |  |  |  | Please.enter.your.child.s.birth.date.: child's birthday (parent reported) |
| Caregiver.1..What.is.the.highest.level.of.education.: education of caregiver 1 (parent reported) |  |  |  | Caregiver.1..What.is.the.highest.level.of.education.: education of caregiver 1 (parent reported) |
| Caregiver.2..What.is.the.highest.level.of.education.: education of caregiver 2 (parent reported) |  |  |  | Caregiver.2..What.is.the.highest.level.of.education.: education of caregiver 2 (parent reported) |
| Is.your.child.currently.going.to.school..If.yes..what.grade...In.the.summer..What.grade.has.your.child.just.completed..: school grade of child (parent reported) |  |  |  | Is.your.child.currently.going.to.school..If.yes..what.grade...In.the.summer..What.grade.has.your.child.just.completed..: school grade of child (parent reported) |
| Which.group.below.most.accurately.describes.your.child.s.ethnic.background.: child's ethnicity (parent reported) |  |  |  | Which.group.below.most.accurately.describes.your.child.s.ethnic.background.: child's ethnicity (parent reported) |
| Which.group.help.most.accurately.describes.your.child.s.racial.background.: child's racial identity (parent reported) |  |  |  | Which.group.help.most.accurately.describes.your.child.s.racial.background.: child's racial identity (parent reported) |
| How.many.days.per.week.does.your.child.spend.using.a.touchscreen.device...e.g..iPad..tablet..smartphone.: days per week child spends using a touchscreen device (parent reported) |  |  |  | How.many.days.per.week.does.your.child.spend.using.a.touchscreen.device...e.g..iPad..tablet..smartphone.: days per week child spends using a touchscreen device (parent reported) |
| On.these.days..how.many.hours.does.your.child.typically.spend.using.the.touchscreen.device.: hours per day child spends on touchscreen device (parent reported) |  |  |  | On.these.days..how.many.hours.does.your.child.typically.spend.using.the.touchscreen.device.: hours per day child spends on touchscreen device (parent reported) |
| Which.types.of.activities.does.your.child.usually.engage.in.on.the.touchscreen.device.: purpose of using touchscreen device (parent reported) |  |  |  | Which.types.of.activities.does.your.child.usually.engage.in.on.the.touchscreen.device.: purpose of using touchscreen device (parent reported) |
| Does.your.child.have.colorblindness.: whether the child is colorblind (parent reported) |  |  |  | Does.your.child.have.colorblindness.: whether the child is colorblind (parent reported) |
| At.what.age.did.your.child.first.begin.to.play.with.a.touchscreen.device.: age child began to use touchscreen device (parent reported) |  |  |  | At.what.age.did.your.child.first.begin.to.play.with.a.touchscreen.device.: age child began to use touchscreen device (parent reported) |
| Have.you.ever.had.any.developmental.concerns.or.have.you.ever.been.referred.to.early.intervention..If.yes..what.it.is.: whether the child has received intervention for developmental concerns (parent reported) |  |  |  | Have.you.ever.had.any.developmental.concerns.or.have.you.ever.been.referred.to.early.intervention..If.yes..what.it.is.: whether the child has received intervention for developmental concerns (parent reported) |
| Does.your.child.hear.any.other.language.other.than.English.on.a.daily.basis..If.yes..which..: other languages child hears besides English (parent reported) |  |  |  | Does.your.child.hear.any.other.language.other.than.English.on.a.daily.basis..If.yes..which..: other languages child hears besides English (parent reported) |

### Load libraries and data

```{r load libs n data}
# Load libraries & general setup
library(tidyverse)
library(ggpubr)
library(ggforce)
library(effectsize)
library(lme4)
library(lmerTest)
library(emmeans)
library(MuMIn)
library(MCMCglmm)
#library(mixedpower)
library(DHARMa)

# Disable scientific notation
options(scipen = 999)

# Read in file
data <- read.csv("data/Experiment2_data.csv", header = TRUE)

# label closing trial
data$condsFile <- ifelse(data$trial == 4, 
                       paste0(data$condsFile, "Closing"), 
                       data$condsFile)

# Read in file for age and combine with data
ages <- read.csv("data/ages.csv", header = T)
data <- left_join(data, ages, by = "participant")

# Make output more interpretable by setting it to sum coding
options(contrasts = c("contr.sum","contr.poly"))

```

## Study time

Preregistration: "Hypotheses will be tested using Generalized Linear Mixed-Effect Models (Lo & Andrews, 2015) with *Condition* as a fixed effect and child (*participant*) as a random intercept, and with appropriate linking functions.

The model for Study Time will have an inverse Gaussian linking function because of its similar distribution to reaction times (Lo & Andrews, 2015)."

### Process data

```{r process study time data}
# Average over all trials for each condition, for each child, as per preregistration
summarized_data <- data %>%
  group_by(participant, condsFile) %>%
  summarize(mean_MU = mean(meanMU, na.rm = TRUE),
            mean_StudyTime = mean(meanListTime, na.rm = TRUE),
            mean_Streak = mean(meanCorBefInc, na.rm = TRUE),
            age = first(Age),
            .groups = 'drop')

# Make sure condition is a factor
summarized_data$condsFile <- as.factor(summarized_data$condsFile)

# Remove closing trials for the free-response only analyses
freeResponseOnly <- summarized_data %>%
  filter(!(condsFile %in% c("noDelayClosing", "longDelayClosing")))
```

### Model study time

```{r study time model}
# Run the model
studyTimeGlmm <- glmer(mean_StudyTime ~ condsFile + (1|participant), 
                         data = freeResponseOnly, 
                         family = inverse.gaussian(link = "identity"))

# Below goes through diagnostic plots and checks
plot(density(freeResponseOnly$mean_StudyTime), 
     xlim=c(0, 160), ylim=c(0, 1), main='M_1 y_hat')
lines(density(predict(studyTimeGlmm, type='response')), col='red')

plot(studyTimeGlmm)

residuals <- residuals(studyTimeGlmm)
qqnorm(residuals)
qqline(residuals, col = "red")

library(performance)
check_model(studyTimeGlmm)


# Below we will compare the full model with the null model
mixConTime_GLMM_null <- glmer(mean_StudyTime ~ 1 + (1|participant), 
                              data = freeResponseOnly, 
                              family = inverse.gaussian(link = "identity"))
mixTimeConAov <- cbind(car::Anova(studyTimeGlmm),
                       r.squaredGLMM(studyTimeGlmm,mixConTime_GLMM_null)) 

# Compare the models
anova(mixConTime_GLMM_null,studyTimeGlmm)

# Get summary
summary(studyTimeGlmm)
mixTimeConAov

# Pairwise comparisons
contrasts(freeResponseOnly$condsFile)
emmeans(studyTimeGlmm, pairwise ~ condsFile)
```

## Memory Usage

Preregistration: "The model for Memory Usage will have an identity linking function because based on the results of our previous studies, we expect it to follow a normal distribution. If there are substantive violations of the assumptions of these analyses, we will corroborate results with analogous non-parametric tests."

```{r model for MU}
# View the distribution of MU
hist(freeResponseOnly$mean_MU)

# Run the model
MU_GLMM <- glmer(mean_MU ~ condsFile + (1|participant),
                 data = freeResponseOnly, 
                    family = gaussian(link = "identity"))

# Below runs diagnostic plots and checks
plot(density(freeResponseOnly$mean_MU), xlim=c(-50, 50), ylim=c(0, 0.6), 
     main='M_1 y_hat')
lines(density(predict(MU_GLMM, type='response') ), col='red')

plot(MU_GLMM)

residuals <- residuals(MU_GLMM)
qqnorm(residuals)
qqline(residuals, col = "red")

check_model(MU_GLMM)

# Compare the full vs the null model
MUfree_null <- glmer(mean_MU ~ 1 + (1|participant), 
                     data = freeResponseOnly, family = gaussian(link = "identity"))
MUfreeAov <- cbind(car::Anova(MU_GLMM),
                   r.squaredGLMM(MU_GLMM,MUfree_null))

anova(MUfree_null,MU_GLMM)

# Get summary
summary(MU_GLMM)
MUfreeAov

# pairwise comparisons
emmeans(MU_GLMM, pairwise ~ condsFile)
```

## Free VS Total response

### Process data

```{r process free v total}
library(dplyr)
# Label cond-type to say if its free or total-response
summarized_data <- summarized_data %>%
  mutate(condType = case_when(
    condsFile %in% c("noDelayClosing", "longDelayClosing") ~ "Total",
    condsFile %in% c("noDelay", "longDelay") ~ "Free",
    TRUE ~ NA_character_
  ))

# Average over participant and condition
freeVtotal <- summarized_data %>%
  group_by(participant, condType) %>%
  summarize(mean_MU = mean(mean_MU, na.rm = TRUE),
            mean_StudyTime = mean(mean_StudyTime, na.rm = TRUE),
            age = first(age),
            .groups = 'drop')
```

### Model free V total

```{r free v total model}
# Observe distribution
hist(freeVtotal$mean_MU)

# Run the model
freeVtotal_glmm <- glmer(mean_MU ~ condType + (1|participant),
                 data = freeVtotal, 
                    family = gaussian(link = "identity"))

# Run diagnostic plots and checks
plot(density(freeVtotal$mean_MU), xlim=c(-50, 50), ylim=c(0, 0.6), 
     main='M_1 y_hat')
lines(density(predict(freeVtotal_glmm, type='response') ), col='red')

plot(freeVtotal_glmm)

residuals <- residuals(freeVtotal_glmm)
qqnorm(residuals)
qqline(residuals, col = "red")

# Compare full with null model
MUfree_null <- glmer(mean_MU ~ 1 + (1|participant), 
                     data = freeVtotal, family = gaussian(link = "identity"))
MUfreeAov <- cbind(car::Anova(freeVtotal_glmm),
                   r.squaredGLMM(freeVtotal_glmm,MUfree_null))

anova(MUfree_null,freeVtotal_glmm)

# Check summary
summary(freeVtotal_glmm)
MUfreeAov
```

## Secondary analyses

### Kendall correlation

"Study time and performance: We will use a Kendall correlation to investigate whether a child’s study time is positively related to MU from all four conditions (No-delay Free-response, Long-delay Free-response, No-delay Total-response, Long-delay Total-response)."

```{r kendall correlation}
# Study time w/ MU(total)
totalResponseOnly <- summarized_data %>%
  filter((condsFile %in% c("noDelayClosing", "longDelayClosing")))
kendall_testTotal <- cor.test(totalResponseOnly$mean_MU, totalResponseOnly$mean_StudyTime, method = "kendall")
kendall_testTotal

# Study time w/ MU(free)
kendall_test <- cor.test(freeResponseOnly$mean_MU, freeResponseOnly$mean_StudyTime, method = "kendall")
kendall_test
```

### Metacognition questions

```{r metacog}
# Set working directory

# Read in data
metacog <- read.csv("data/metacog_exp2.csv",header=TRUE)

# Only get participants who were included in analyses
metacog_d <- metacog[metacog$Participant %in% freeResponseOnly$participant, ]

# Get tables for kids responses
# Q: Which game did you think was harder?
metaSum <- cbind(harder= table(metacog_d$Harder_clean)) %>% data.frame()
# Q: When the store was closing, did the game get harder?
metaSumClosing <- cbind(Closing= table(metacog_d$Closing_harder_clean)) %>% data.frame()
# Q: When the store was closing, did you feel like you were guessing or not?
metaSumGuess <- cbind(Guess = table(metacog_d$Guess_clean)) %>% data.frame()

# Run binomial tests on answers
harderTest <- binom.test(metaSum$harder[2],sum(metaSum$harder),0.5)
closingTest <- binom.test(metaSumClosing$Closing[2],sum(metaSumClosing$Closing),0.5)
guessTest <- binom.test(metaSumGuess$Guess[2],sum(metaSumGuess$Guess),0.5)

harderTest
closingTest
guessTest
```

### Open-ended strategy question

```{r open ended answers}
all_kids <- read.csv("data/lastQ_everyone.csv", header = T)

# Only included participants
all_kids <- all_kids[all_kids$Participant %in% data$participant, ]

# Order by age
all_kids <- all_kids[order(all_kids$Age), ]
```

### Equivalence test for MU(free) vs MU(total)

**Test**: paired TOSTER t-test with a smallest-effect-size-of-interest (SESOI) of Cohen's dz = 0.4

```{r tost test of mufree n total}
library(TOSTER)

t_TOST(mean_MU ~ condType, data = freeVtotal, paired = TRUE,
       eqb = 0.4, eqbound_type = "SMD")
```

### Effect size

```{r effect sizes}

## Eta squared
library(effectsize)
model <- lmer(mean_StudyTime ~ condsFile + (1 | participant), data = freeResponseOnly)
eta_squared(model)

model <- lmer(mean_MU  ~ condsFile + (1 | participant), data = freeResponseOnly)
eta_squared(model)

model <- lmer(mean_MU  ~ condType  + (1 | participant), data = freeVtotal)
eta_squared(model)
```

## Supplementary Material

### Screen use

```{r screen use}
# Group by participant
participant_data <- data %>%
  group_by(participant) %>%
  slice(1) %>%
    ungroup()

# Organize into numeric data
participant_data <- participant_data %>%
  mutate(screen_use_numeric = case_when(
    On.these.days..how.many.hours.does.your.child.typically.spend.using.the.touchscreen.device. == "0" ~ 0,
    On.these.days..how.many.hours.does.your.child.typically.spend.using.the.touchscreen.device. == "0-1 hour" ~ 1,
    On.these.days..how.many.hours.does.your.child.typically.spend.using.the.touchscreen.device. == "1-2 hours" ~ 2,
    On.these.days..how.many.hours.does.your.child.typically.spend.using.the.touchscreen.device. == "2-3 hours" ~ 3,
    TRUE ~ NA_real_
  ))

# Get mean and SD
mean(participant_data$screen_use_numeric, na.rm = T)
sd(participant_data$screen_use_numeric, na.rm = T)
```

### All trips

```{r all trips process data}
# Read in file
data <- read.csv("data/Experiment2_allTrips.csv", header = TRUE)

# label closing trial
data$condsFile <- ifelse(data$trial == 4, 
                       paste0(data$condsFile, "Closing"), 
                       data$condsFile)

# Read in file for age and combine with data
ages <- read.csv("data/ages.csv", header = T)
data <- left_join(data, ages, by = "participant")

# Get mean and sd for each condition
mean(data$meanMU[data$condsFile == "noDelay"])
sd(data$meanMU[data$condsFile == "noDelay"])

mean(data$meanMU[data$condsFile == "longDelay"])
sd(data$meanMU[data$condsFile == "longDelay"])

# study time
mean(data$meanListTime[data$condsFile == "noDelay"])
sd(data$meanListTime[data$condsFile == "noDelay"])

mean(data$meanListTime[data$condsFile == "longDelay"])
sd(data$meanListTime[data$condsFile == "longDelay"])

```

#### Study time

```{r all trips study time}
# Average over all trials for each condition, for each child, as per preregistration
summarized_data <- data %>%
  group_by(participant, condsFile) %>%
  summarize(mean_MU = mean(meanMU, na.rm = TRUE),
            mean_StudyTime = mean(meanListTime, na.rm = TRUE),
            mean_Streak = mean(meanCorBefInc, na.rm = TRUE),
            age = first(Age),
            .groups = 'drop')

# make sure condition is a factor
summarized_data$condsFile <- as.factor(summarized_data$condsFile)

# Remove closing trials
freeResponseOnly_all <- summarized_data %>%
  filter(!(condsFile %in% c("noDelayClosing", "longDelayClosing")))

# Run the model
studyTime_all <- glmer(mean_StudyTime ~ condsFile + (1|participant), 
                         data = freeResponseOnly_all, 
                         family = inverse.gaussian(link = "identity"))

# Full VS null
mixConTime_GLMM_null <- glmer(mean_StudyTime ~ 1 + (1|participant), 
                              data = freeResponseOnly_all, 
                              family = inverse.gaussian(link = "identity"))

mixTimeConAov <- cbind(car::Anova(studyTime_all),
                       r.squaredGLMM(studyTime_all,mixConTime_GLMM_null)) 

# Effect size
library(effectsize)
model <- lmer(mean_StudyTime ~ condsFile + (1|participant), 
                         data = freeResponseOnly_all)
eta_squared(model)
```

#### MU

```{r all trips mu}
# Run the model
MU_GLMM <- glmer(mean_MU ~ condsFile + (1|participant),
                 data = freeResponseOnly_all, 
                    family = gaussian(link = "identity"))

# Full VS null
MUfree_null <- glmer(mean_MU ~ 1 + (1|participant), 
                     data = freeResponseOnly_all, family = gaussian(link = "identity"))
MUfreeAov <- cbind(car::Anova(MU_GLMM),
                   r.squaredGLMM(MU_GLMM,MUfree_null))

# Effect size
model <- lmer(mean_MU ~ condsFile + (1|participant), 
                         data = freeResponseOnly_all)
eta_squared(model)
```

### Comparisons with Liang et al.

Trips

```{r trips}
# Read in file
all_trips <- read.csv("data/Experiment2_allTrips.csv", header = TRUE)

# Get mean and SD
mean(all_trips$nTrip[all_trips$condsFile == "noDelay"],)
mean(all_trips$nTrip[all_trips$condsFile == "longDelay"],)
sd(all_trips$nTrip[all_trips$condsFile == "noDelay"],)
sd(all_trips$nTrip[all_trips$condsFile == "longDelay"],)
```

Streak correct

```{r streak}
# Get mean and SD
mean(freeResponseOnly$mean_Streak[freeResponseOnly$condsFile == "noDelay"],)
mean(freeResponseOnly$mean_Streak[freeResponseOnly$condsFile == "longDelay"],)
sd(freeResponseOnly$mean_Streak[freeResponseOnly$condsFile == "noDelay"],)
sd(freeResponseOnly$mean_Streak[freeResponseOnly$condsFile == "longDelay"],)
```

### Additional measures

The following describes the mean and standard deviation for the number of attempts children made on first trips in each condition, the mean and standard deviation for the amount of time children spent in the store for each condition, and the mean and standard deviation for the number of trips in each condition.

```{r additional measures}
# Number of attempts
add_measures <- data %>%
  group_by(participant, condsFile) %>%
  summarize(mean_Attempts = mean(totalClickeds, na.rm = TRUE),
            mean_shelfTime = mean(meanShelfTime, na.rm = TRUE),
            .groups = 'drop')

# Rename Closing trials as Total-response
add_measures <- add_measures %>%
  mutate(condsFile = case_when(
    condsFile %in% c("noDelayClosing", "longDelayClosing") ~ "totalResponse",
    TRUE ~ condsFile  # Keep the original value for all other cases
  ))

# Trips
# Load file
allTrips <- read.csv("data/Experiment2_allTrips.csv", header = TRUE)

# label closing trial
allTrips$condsFile <- ifelse(allTrips$trial == 4, 
                       paste0(allTrips$condsFile, "Closing"), 
                       allTrips$condsFile)

# Rename Closing trials as Total-response
allTrips <- allTrips %>%
  mutate(condsFile = case_when(
    condsFile %in% c("noDelayClosing", "longDelayClosing") ~ "totalResponse",
    TRUE ~ condsFile  # Keep the original value for all other cases
  ))

trips <- allTrips %>%
  group_by(participant, condsFile) %>%
  summarize(meanTrips = mean(nTrip, na.rm = TRUE),
            .groups = 'drop')

# Get N, change condition as needed
add_measures %>%
  filter(condsFile == "totalResponse", !is.na(mean_Attempts)) %>%
  summarise(n_unique = n_distinct(participant))

# Mean and standard deviation for each
# attempts
mean(add_measures$mean_Attempts[add_measures$condsFile == "noDelay"])
sd(add_measures$mean_Attempts[add_measures$condsFile == "noDelay"])

mean(add_measures$mean_Attempts[add_measures$condsFile == "longDelay"])
sd(add_measures$mean_Attempts[add_measures$condsFile == "longDelay"])

mean(add_measures$mean_Attempts[add_measures$condsFile == "totalResponse"])
sd(add_measures$mean_Attempts[add_measures$condsFile == "totalResponse"])

# shelf time
mean(add_measures$mean_shelfTime[add_measures$condsFile == "noDelay"])
sd(add_measures$mean_shelfTime[add_measures$condsFile == "noDelay"])

mean(add_measures$mean_shelfTime[add_measures$condsFile == "longDelay"])
sd(add_measures$mean_shelfTime[add_measures$condsFile == "longDelay"])

mean(add_measures$mean_shelfTime[add_measures$condsFile == "totalResponse"])
sd(add_measures$mean_shelfTime[add_measures$condsFile == "totalResponse"])

# trips
mean(trips$meanTrips[trips$condsFile == "noDelay"])
sd(trips$meanTrips[trips$condsFile == "noDelay"])

mean(trips$meanTrips[trips$condsFile == "longDelay"])
sd(trips$meanTrips[trips$condsFile == "longDelay"])

mean(trips$meanTrips[trips$condsFile == "totalResponse"])
sd(trips$meanTrips[trips$condsFile == "totalResponse"])
```

### Random effects comparisons

Study time:

```{r study time random effects}
# Make sure condition is a factor
data$condsFile <- as.factor(data$condsFile)

# Remove closing trials for the free-response only analyses
freeResponseOnly <- data %>%
  filter(!(condsFile %in% c("noDelayClosing", "longDelayClosing")))

# Maximal model
studytime_m1 <- glmer(meanListTime ~ condsFile + (1 + condsFile|participant) + (1|trial), 
                        data = freeResponseOnly, 
                        family = inverse.gaussian(link = "identity"))

# Using repca, assess dimensionality
rePCA(studytime_m1)
```

Memory Use:

```{r random effects memory use}
# Maximal model
MU_m1 <- lmer(meanMU ~ condsFile + (1 + condsFile|participant) + (1|trial), 
                        data = freeResponseOnly)

# Model without correlations between slopes and intercept
MU_m2 <- lmer(meanMU ~ condsFile + (1|participant) + (0 + condsFile|participant) + (1|trial), 
                        data = freeResponseOnly)

# Model with slopes and no intercept
MU_m3 <- lmer(meanMU ~ condsFile + (0 + condsFile|participant) + (1|trial), 
                data = freeResponseOnly)

# Only participant and trial intercepts
MU_m4 <- lmer(meanMU ~ condsFile + (1|participant) + (1|trial), 
                data = freeResponseOnly)

# Only slopes
MU_m5 <- lmer(meanMU ~ condsFile + (1 + condsFile|participant), 
                data = freeResponseOnly)

# Using repca, assess dimensionality
rePCA(MU_m5)
```

Free Vs. Total Response Memory Use

```{r free v total random effects}
# Label cond-type to say if its free or total-response
data <- data %>%
  mutate(condType = case_when(
    condsFile %in% c("noDelayClosing", "longDelayClosing") ~ "Total",
    condsFile %in% c("noDelay", "longDelay") ~ "Free",
    TRUE ~ NA_character_
  ))

# Maximal model
fVt_m1 <- lmer(meanMU ~ condType + (1 + condType|participant) + (1|trial), 
                data = data)

# Model without correlations between slopes and intercept
fVt_m2 <- lmer(meanMU ~ condType + (1|participant) + (0 + condType|participant) + (1|trial), 
                data = data)

# Model with slopes and no intercept
fVt_m3 <- lmer(meanMU ~ condType + (0 + condType|participant) + (1|trial), 
                data = data)

# Only participant and trial intercepts
fVt_m4 <- lmer(meanMU ~ condType + (1|participant) + (1|trial), 
                data = data)

# Only slopes
fVt_m5 <- lmer(meanMU ~ condType + (1 + condType|participant), 
                data = data)
```

## Plots

##### Figure 9, MU and Study time between conditions

```{r fig 9}
par(mfrow = c(1, 2))

# 95% CI function
ci95 <- function(x) {
  x <- x[!is.na(x)]
  m  <- mean(x)
  se <- sd(x) / sqrt(length(x))
  # t-critical value for 95 % CI
  tcrit <- qt(0.975, df = length(x) - 1)
  c(lower = m - tcrit * se,
    upper = m + tcrit * se)
}

# Rename values in the 'condsFile' column
freeResponseOnly$condsFile <- as.character(freeResponseOnly$condsFile)
freeResponseOnly$condsFile[freeResponseOnly$condsFile == "noDelay"] <- "No-delay"
freeResponseOnly$condsFile[freeResponseOnly$condsFile == "longDelay"] <- "Long-delay"

# study time ------------
# Calculate means
means <- tapply(freeResponseOnly$mean_StudyTime, freeResponseOnly$condsFile, mean)

# Define the x-axis levels (to match the ggplot2 ordering)
conds_levels <- c("No-delay", "Long-delay")
x_positions <- 1:length(conds_levels)

# Create an empty plot
plot(
  x_positions, means[conds_levels], 
  type = "n", xaxt = "n", yaxt = "n", ylim = c(0, 20.0), xlim = c(0.5, 2.5),
  xlab = "", ylab = "Mean Study Time (seconds)", 
  main = "",
    cex.lab = 1.2,
  cex.axis = 1.2,
  cex.main = 1.1
)

axis(2, at = seq(0, 20, by = 4), cex.axis = 1.2)

participants <- unique(freeResponseOnly$participant)

for (p in participants) {
  this_participant <- freeResponseOnly[freeResponseOnly$participant == p, ]
  if (nrow(this_participant) == 2) {
    # Get the x positions for this participant’s conditions
    x_vals <- match(this_participant$condsFile, conds_levels)
    y_vals <- this_participant$mean_StudyTime
    lines(x_vals, y_vals, col = adjustcolor("#009E73", alpha.f = 0.3), lwd = 1)
  }
}

# Add x-axis labels normally
axis(1, at = x_positions, labels = conds_levels, cex.axis = 1.2)

# Add points for each participant
for (i in 1:length(conds_levels)) {
  condition_data <- freeResponseOnly[freeResponseOnly$condsFile == conds_levels[i], ]
  points(rep(x_positions[i], nrow(condition_data)), condition_data$mean_StudyTime, 
         pch = 1, col = "#0072B2")
}

# Add points for the means
points(x_positions, means[conds_levels], pch = 10, col = "black")

# Add a solid line connecting the means
#lines(x_positions, means[conds_levels], col = "black", lwd = 2)

# Add horizontal segments at the means (optional, similar to ggplot2's stat_summary)
segments(
  x_positions - 0.1, means[conds_levels], 
  x_positions + 0.1, means[conds_levels],
  col = "black", lwd = 3.0
)

# Add mean labels for each condition
#text(x_positions, means[conds_levels] + 3, 
#     labels = round(means[conds_levels], 2), cex = 1.5, col = "black")

# Get means again, just to be sure
means <- tapply(freeResponseOnly$mean_StudyTime, freeResponseOnly$condsFile, mean)

# Compute CIs by condition
cis <- tapply(freeResponseOnly$mean_StudyTime, freeResponseOnly$condsFile, ci95)

# Pull lower and upper bounds in plotting order
lower_bounds <- sapply(cis[conds_levels], function(x) x["lower"])
upper_bounds <- sapply(cis[conds_levels], function(x) x["upper"])

# Add vertical error bars using arrows()
for (i in 1:length(x_positions)) {
  arrows(
    x0 = x_positions[i], y0 = lower_bounds[i], 
    x1 = x_positions[i], y1 = upper_bounds[i], 
    length = 0.1, angle = 90, code = 3, col = "#D55E00", lwd = 3.5
  )
}

# memory usage -----------
# Calculate means and standard errors
means <- tapply(freeResponseOnly$mean_MU, freeResponseOnly$condsFile, mean)

# Calculate standard deviations and sample sizes for each condition
sds <- tapply(freeResponseOnly$mean_MU, freeResponseOnly$condsFile, sd)
n_per_condition <- tapply(freeResponseOnly$mean_MU, freeResponseOnly$condsFile, length)

# Calculate standard errors
se <- sds / sqrt(n_per_condition)

# Define the x-axis levels (to match the ggplot2 ordering)
conds_levels <- c("No-delay", "Long-delay")
x_positions <- 1:length(conds_levels)

# Create an empty plot
plot(
  x_positions, means[conds_levels], 
  type = "n", xaxt = "n", yaxt = "n", ylim = c(-1, 8.0), xlim = c(0.5, 2.5),
  xlab = "", ylab = "Mean Memory Usage (items)", 
  main = "",
    cex.lab = 1.2,
  cex.axis = 1.2,
  cex.main = 1.1
)

axis(2, at = seq(-1, 8, by = 1), labels = ifelse(seq(-1, 8, by = 1) %% 2 == 0, seq(-1, 8, by = 1), ""), cex.axis = 1.2)

participants <- unique(freeResponseOnly$participant)

for (p in participants) {
  this_participant <- freeResponseOnly[freeResponseOnly$participant == p, ]
  if (nrow(this_participant) == 2) {
    # Get the x positions for this participant’s conditions
    x_vals <- match(this_participant$condsFile, conds_levels)
    y_vals <- this_participant$mean_MU
    lines(x_vals, y_vals, col = adjustcolor("#009E73", alpha.f = 0.3), lwd = 1)
  }
}


# Add x-axis labels normally
axis(1, at = x_positions, labels = conds_levels, cex.axis = 1.2)

# Add points for each participant
for (i in 1:length(conds_levels)) {
  condition_data <- freeResponseOnly[freeResponseOnly$condsFile == conds_levels[i], ]
  points(rep(x_positions[i], nrow(condition_data)), condition_data$mean_MU, 
         pch = 1, col = "#0072B2")
}

# Add points for the means
points(x_positions, means[conds_levels], pch = 10, col = "black")

# Add a solid line connecting the means
#lines(x_positions, means[conds_levels], col = "black", lwd = 2)

# Add horizontal segments at the means (optional, similar to ggplot2's stat_summary)
segments(
  x_positions - 0.1, means[conds_levels], 
  x_positions + 0.1, means[conds_levels],
  col = "black", lwd = 3.0
)

# Add mean labels for each condition
#text(x_positions, means[conds_levels] + 2, 
#     labels = round(means[conds_levels], 2), cex = 1.5, col = "black")

# Get means again, just to be sure
means <- tapply(freeResponseOnly$mean_MU, freeResponseOnly$condsFile, mean)

# Compute CIs by condition
cis <- tapply(freeResponseOnly$mean_MU, freeResponseOnly$condsFile, ci95)

# Pull lower and upper bounds in plotting order
lower_bounds <- sapply(cis[conds_levels], function(x) x["lower"])
upper_bounds <- sapply(cis[conds_levels], function(x) x["upper"])

# Add vertical error bars
for (i in seq_along(x_positions)) {
  arrows(
    x0 = x_positions[i], y0 = lower_bounds[i], 
    x1 = x_positions[i], y1 = upper_bounds[i], 
    length = 0.1, angle = 90, code = 3, col = "#D55E00", lwd = 3.5
  )
}
```

##### Figure 10, MU(free) vs MU(total)

```{r mu free v total}
# Calculate means and standard errors
means <- tapply(freeVtotal$mean_MU, freeVtotal$condType, mean)

# Calculate standard deviations and sample sizes for each condition
sds <- tapply(freeVtotal$mean_MU, freeVtotal$condType, sd)
n_per_condition <- tapply(freeVtotal$mean_MU, freeVtotal$condType, length)

# Calculate standard errors
se <- sds / sqrt(n_per_condition)

# Define the x-axis levels (to match the ggplot2 ordering)
conds_levels <- c("Free", "Total")
x_positions <- 1:length(conds_levels)

# Create an empty plot
plot(
  x_positions, means[conds_levels], 
  type = "n", xaxt = "n", yaxt = "n", ylim = c(-5, 10.0), xlim = c(0.5, 2.5),
  xlab = "", ylab = "Mean Memory Usage (items)", 
  main = "",
  cex.lab = 1.1,
  cex.axis = 1.5,
  cex.main = 1.1
)

axis(2, at = seq(-5, 10, by = 5), labels = seq(-5, 10, by = 5), cex.axis = 1.2)

participants <- unique(freeVtotal$participant)

for (p in participants) {
  this_participant <- freeVtotal[freeVtotal$participant == p, ]
  if (nrow(this_participant) == 2) {
    # Get the x positions for this participant’s conditions
    x_vals <- match(this_participant$condType, conds_levels)
    y_vals <- this_participant$mean_MU
    lines(x_vals, y_vals, col = adjustcolor("#009E73", alpha.f = 0.3), lwd = 1)
  }
}

# Add x-axis labels normally
axis(1, at = x_positions, labels = conds_levels, cex.axis = 1.2)

# Add points for each participant
for (i in 1:length(conds_levels)) {
  condition_data <- freeVtotal[freeVtotal$condType == conds_levels[i], ]
  points(rep(x_positions[i], nrow(condition_data)), condition_data$mean_MU, 
         pch = 1, col = "#0072B2")
}

# Add points for the means
points(x_positions, means[conds_levels], pch = 10, col = "black")

# Add a solid line connecting the means
#lines(x_positions, means[conds_levels], col = "black", lwd = 2)

# Add horizontal segments at the means (optional, similar to ggplot2's stat_summary)
segments(
  x_positions - 0.1, means[conds_levels], 
  x_positions + 0.1, means[conds_levels],
  col = "black", lwd = 3.0
)

# Add mean labels for each condition
#text(x_positions, means[conds_levels] + 2, 
#     labels = round(means[conds_levels], 2), cex = 1.5, col = "black")

# Get means again, just to be sure
means <- tapply(freeVtotal$mean_MU, freeVtotal$condType, mean)

# Compute CIs by condition
cis <- tapply(freeVtotal$mean_MU, freeVtotal$condType, ci95)

# Pull lower and upper bounds in plotting order
lower_bounds <- sapply(cis[conds_levels], function(x) x["lower"])
upper_bounds <- sapply(cis[conds_levels], function(x) x["upper"])

# Add vertical error bars
for (i in seq_along(x_positions)) {
  arrows(
    x0 = x_positions[i], y0 = lower_bounds[i], 
    x1 = x_positions[i], y1 = upper_bounds[i], 
    length = 0.1, angle = 90, code = 3, col = "#D55E00", lwd = 3.5
  )
}
```
