---
title: "Experiment_1_analysis"
format: html
editor: visual
---

# Main analyses

How much do you remember when it’s up to you? Measuring memory use without response bias in young children

Last edited: 10/3/25

In this file there is the preregistered main analyses, secondary analyses, as well as the analyses and descriptive statistics used for the supplementary materials.

Variable and data descriptions:

+---------------------------------------------------------------------------------------------------------------------------------+----------------------------------------------------------------------------+---------------------------------------------------------------------------------------------------------------------------------+
| Experiment1_data.csv                                                                                                            | metacog.csv                                                                | Experiment1_allTrips.csv                                                                                                        |
+=================================================================================================================================+============================================================================+=================================================================================================================================+
| |  |                                                                                                                            | |                                                                        | | |  |                                                                                                                            |
| |----|                                                                                                                          | |------------------------------------------------------------------------| | |----|                                                                                                                          |
| | participant: participant ID |                                                                                                 | | participant: participant ID                                            | | | participant: participant ID |                                                                                                 |
| | condsFile: condition |                                                                                                        | | easy: child's answer to which condition was easier                     | | | condsFile: condition |                                                                                                        |
| | order: counterbalanced order |                                                                                                | | again: child's answer to which condition they would like to play again | | | order: counterbalanced order |                                                                                                |
| | trial: trial number |                                                                                                         | | strategy: child's answer to the fourth, open ended strategy question   | | | trial: trial number |                                                                                                         |
| | nTrip: trip ID (always 1) |                                                                                                   |                                                                            | | nTrip: trip ID |                                                                                                              |
| | totalListTime: absolute time studying the list |                                                                              |                                                                            | | totalListTime: absolute time studying the list |                                                                              |
| | meanListTime: average time studying the list (same as totalListTime since this data is for first-trips only) |                |                                                                            | | meanListTime: average time studying the list |                                                                                |
| | totalShelfTime: absolute time selecting items in the store |                                                                  |                                                                            | | totalShelfTime: absolute time selecting items in the store |                                                                  |
| | meanShelfTime: average selecting items in the store (same as totalShelf Time since this data is for first-trips only) |       |                                                                            | | meanShelfTime: average selecting items in the store |                                                                         |
| | totalTime: absolute time in the first trip studying the list and selecting items in the store |                               |                                                                            | | totalTime: absolute time in the first trip studying the list and selecting items in the store |                               |
| | totalCorrect: sum of correct selections |                                                                                     |                                                                            | | totalCorrect: sum of correct selections |                                                                                     |
| | meanCorrect: mean of correct selections (same as totalCorrect since this data is for first-trips only) |                      |                                                                            | | meanCorrect: mean of correct selections |                                                                                     |
| | meanCorBefInc: mean correct selections before making an incorrect selection |                                                 |                                                                            | | meanCorBefInc: mean correct selections before making an incorrect selection |                                                 |
| | totalInCorrect: sum of incorrect selections |                                                                                 |                                                                            | | totalInCorrect: sum of incorrect selections |                                                                                 |
| | meanIncorrect: mean of incorrect selections (same as totalInCorrect since this data is for first-trips only) |                |                                                                            | | meanIncorrect: mean of incorrect selections |                                                                                 |
| | maxCorrect: maximum amount of correct selections (same as totalCorrect since this data is for first-trips only) |             |                                                                            | | maxCorrect: maximum amount of correct selections |                                                                            |
| | maxIncorrect: maximum amount of incorrect selections (same as totalInCorrect since this data is for first-trips only) |       |                                                                            | | maxIncorrect: maximum amount of incorrect selections |                                                                        |
| | totalClickeds: sum of all selections made |                                                                                   |                                                                            | | totalClickeds: sum of all selections made |                                                                                   |
| | meanclickeds: mean of all selections made (same as totalClickeds since this data is for first-trips only) |                   |                                                                            | | meanclickeds: mean of all selections made |                                                                                   |
| | meanMU: average value of Memory Use |                                                                                         |                                                                            | | meanMU: average value of Memory Use |                                                                                         |
| | datetime: day and time of testing |                                                                                           |                                                                            | | datetime: day and time of testing |                                                                                           |
| | Gender: gender of participant |                                                                                               |                                                                            | | Gender: gender of participant |                                                                                               |
| | Parent_reported_age: age that parent reported in the demographic form |                                                       |                                                                            | | Parent_reported_age: age that parent reported in the demographic form |                                                       |
| | Grade: school grade of participant (parent-reported) |                                                                        |                                                                            | | Grade: school grade of participant (parent-reported) |                                                                        |
| | Ethnicity: ethnicity of participant (parent-reported) |                                                                       |                                                                            | | Ethnicity: ethnicity of participant (parent-reported) |                                                                       |
| | Race: race of participant (parent-reported) |                                                                                 |                                                                            | | Race: race of participant (parent-reported) |                                                                                 |
| | screen_use_days: number of days with which the child uses a touchscreen device (parent-reported) |                            |                                                                            | | screen_use_days: number of days with which the child uses a touchscreen device (parent-reported) |                            |
| | screen_use_hour: number of hours with which the child uses a touchscreen device on a given day (parent-reported) |            |                                                                            | | screen_use_hour: number of hours with which the child uses a touchscreen device on a given day (parent-reported) |            |
| | screen_purpose: purpose for which the child uses a touchscreen device (parent-reported) |                                     |                                                                            | | screen_purpose: purpose for which the child uses a touchscreen device (parent-reported) |                                     |
| | colorblindness: whether the child is colorblind (parent-reported) |                                                           |                                                                            | | colorblindness: whether the child is colorblind (parent-reported) |                                                           |
| | screen_age_started: age at which the child began to use a touchscreen device (parent-reported) |                              |                                                                            | | screen_age_started: age at which the child began to use a touchscreen device (parent-reported) |                              |
| | intervention: whether the child has received professional intervention for developmental related concerns (parent-reported) | |                                                                            | | intervention: whether the child has received professional intervention for developmental related concerns (parent-reported) | |
| | languages: languages the child hears at home besides English (parent-reported) |                                              |                                                                            | | languages: languages the child hears at home besides English (parent-reported) |                                              |
| | birthday.x: parent-reported birthday on demographic form |                                                                    |                                                                            | | birthday.x: parent-reported birthday on demographic form |                                                                    |
| | birthday.y: experimenter-reported birthday from asking parent directly |                                                      |                                                                            | | birthday.y: experimenter-reported birthday from asking parent directly |                                                      |
| | age: rounded age of participant |                                                                                             |                                                                            | | age: rounded age of participant |                                                                                             |
| | date: day of testing |                                                                                                        |                                                                            | | date: day of testing |                                                                                                        |
| | months: age of child in months |                                                                                              |                                                                            | | months: age of child in months |                                                                                              |
| | days: days to add to months to get exact child age at day of testing |                                                        |                                                                            | | days: days to add to months to get exact child age at day of testing |                                                        |
| | agebin: binned age category of child |                                                                                        |                                                                            | | agebin: binned age category of child |                                                                                        |
| | conditionType: whether the condition was free-response or total-response |                                                    |                                                                            |                                                                                                                                 |
+---------------------------------------------------------------------------------------------------------------------------------+----------------------------------------------------------------------------+---------------------------------------------------------------------------------------------------------------------------------+

## Process data

```{r process data}
# Load libraries & general setup
library(tidyverse)
library(ggpubr)
library(ggforce)
library(effectsize)
library(lme4)
library(lmerTest)
library(emmeans)
library(MuMIn)
library(MCMCglmm)
library(DHARMa)

# Disable scientific notation
options(scipen = 999)

# Load file
multiDataTrialSum1Trip <- read.csv("data/Experiment1_data.csv", header = TRUE)

# Remove the old One-shot block
# (See Supplementary Table S1, S2, S3, S4)
no1shot <- multiDataTrialSum1Trip %>%
  filter(!condsFile == "oneShot3.2") %>%
  filter(!condsFile == "oneShotClosing")

# Rename Closing trials as Total-response
# (See Supplementary Table S1)
data <- no1shot %>%
  mutate(condsFile = case_when(
    condsFile %in% c("noDelayClosing", "longDelayClosing") ~ "totalResponse",
    TRUE ~ condsFile  # Keep the original value for all other cases
  ))

# Make output more interpretable by using sum coding
options(contrasts = c("contr.sum","contr.poly"))
```

## Study time

Preregistration: "Unless specified otherwise, hypotheses will be tested using Generalized Linear Mixed-Effect Models (Lo & Andrews, 2015) with Condition and Age as fixed effects and participant as a random effect, and with appropriate linking functions. If there are substantive violations of the assumptions of these analyses, we will corroborate results with non-parametric tests."

```{r study time model}
# Average over all trials for each condition, for each child, as per preregistration
study_time <- data %>%
  group_by(participant, condsFile) %>%
  summarize(mean_MU = mean(meanMU, na.rm = TRUE),
            mean_StudyTime = mean(meanListTime, na.rm = TRUE), 
            age = first(age), 
            .groups = 'drop')

# Center age
study_time$age.ct <- study_time$age - mean(study_time$age)

# make sure condition is a factor
study_time$condsFile <- as.factor(study_time$condsFile)

# Run model
studyTimeGlmm <- glmer(mean_StudyTime ~ condsFile + age.ct + age.ct*condsFile + (1|participant), 
                         data = study_time, 
                         family = inverse.gaussian(link = "identity"), nAGQ = 0)

# Below runs model diagnostic plots and tests
plot(density(study_time$mean_StudyTime), xlim=c(0, 160), ylim=c(0, 1), main='M_1 y_hat')
lines(density(predict(studyTimeGlmm, type='response')), col='red')

plot(studyTimeGlmm)

residuals <- residuals(studyTimeGlmm)
qqnorm(residuals)
qqline(residuals, col = "red")

# Below we will compare model with one that has no fixed effects
# To see if the fixed effects (condsFile) is important at explaining the data
mixConTime_GLMM_null <- glmer(mean_StudyTime ~ 1 + (1|participant), 
                              data = study_time, 
                              family = inverse.gaussian(link = "identity"), nAGQ = 0)
mixTimeConAov <- cbind(car::Anova(studyTimeGlmm),
                       r.squaredGLMM(studyTimeGlmm,mixConTime_GLMM_null)) 

# Compare the models
anova(mixConTime_GLMM_null,studyTimeGlmm)

# Look at the summary
summary(studyTimeGlmm)
mixTimeConAov

# Pairwise comparisons
contrasts(study_time$condsFile)
emmeans(studyTimeGlmm, pairwise ~ condsFile)

# Make No-delay the reference
study_timeLD <- study_time
study_timeLD$condsFile <- relevel(study_time$condsFile, ref = "longDelay")

studyTimeGlmmLD <- glmer(mean_StudyTime ~ condsFile + age.ct + age.ct*condsFile + 
                         (1|participant), 
                       data = study_timeLD, 
                       family = inverse.gaussian(link = "identity"), 
                       nAGQ = 0)

# Simple linear regression with difference score for age-of-emergence
# (For the manuscript, this was done in Prism, but here is an R approximation)

# Remove Long-delay condition
No_LD <- study_time %>% filter(!condsFile %in% "longDelay")

# Select relevant columns for Study time regression
No_LD_wide_ST <- No_LD %>% 
  select(participant, condsFile, mean_StudyTime, age, age.ct) 

# Make wide
No_LD_wide_ST <- pivot_wider(No_LD_wide_ST, names_from = condsFile, values_from = mean_StudyTime)

# Get difference scores
No_LD_wide_ST$diffscores <- No_LD_wide_ST$totalResponse - No_LD_wide_ST$noDelay

# Remove NA's
noNA_ST <- na.omit(No_LD_wide_ST)

# Regression for Study time
ST_model <- lm(diffscores ~ age, data = noNA_ST)

# Plot
pStudytime <- ggplot(noNA_ST, aes(x=age, y=diffscores)) +
  geom_point() +
  geom_smooth(method=lm , color="black", fill="grey", se=TRUE) +
  scale_y_continuous(limits = c(-5,15)) +
  theme_classic()

library(car)
# x-intercept is -b0/b1
deltaMethod(ST_model, "-(Intercept)/age", level = 0.95)

## Calculate leverage of age
#calculate leverage for each observation in the model
hats <- as.data.frame(hatvalues(ST_model))
```

## Memory Use

```{r mu model}
# Average over participant and condition
MU_data <- data %>%
  group_by(participant, condsFile) %>%
  summarize(mean_MU = mean(meanMU, na.rm = TRUE), 
            age = first(age), 
            .groups = 'drop')

# Center age
MU_data$age.ct <- MU_data$age - mean(MU_data$age)

# make sure condition is a factor
MU_data$condsFile <- as.factor(MU_data$condsFile)

# Reference level should be One-shot
MU_data$condsFile <- factor(
  MU_data$condsFile,
  levels = c("longDelay", "noDelay", "totalResponse")
)
contrasts(MU_data$condsFile) <- contr.sum(3)

# Run the model
MU_GLMM <- lmer(mean_MU ~ condsFile + age.ct + age.ct*condsFile + (1|participant), 
                    data = MU_data)

# Below runs model diagnostic plots and tests
plot(density(MU_data$mean_MU), xlim=c(-50, 50), ylim=c(0, 0.6), main='M_1 y_hat')
lines(density(predict(MU_GLMM, type='response') ), col='red')

plot(MU_GLMM)

residuals <- residuals(MU_GLMM)
qqnorm(residuals)
qqline(residuals, col = "red")

# Summary
library(lmerTest)
summary(MU_GLMM)

# Get the p value, and R squared
MUfree_null <- glmer(mean_MU ~ 1 + (1|participant), 
                     data = MU_data, family = gaussian(link = "identity"))
MUfreeAov <- cbind(car::Anova(MU_GLMM),
                   r.squaredGLMM(MU_GLMM,MUfree_null))

MUfreeAov

# Comparing if the full fits better than the null model
anova(MUfree_null,MU_GLMM)

# Pairwise comparisons
library(emmeans)
emmeans(MU_GLMM, list(pairwise ~ condsFile), adjust = "tukey")

# Simple linear regression with difference score for age-of-emergence

# Select relevant columns for Memory use regression
No_LD_wide_MU <- No_LD %>% 
  select(participant, condsFile, mean_MU, age, age.ct)

# Made wide
No_LD_wide_MU <- pivot_wider(No_LD_wide_MU, names_from = condsFile, values_from = mean_MU)

# Get difference scores
No_LD_wide_MU$diffscores <- No_LD_wide_MU$totalResponse - No_LD_wide_MU$noDelay

# Remove NA's
noNA_MU <- na.omit(No_LD_wide_MU)

# Regression for Memory use
MU_model <- lm(diffscores ~ age, data = noNA_MU)

pMU <- ggplot(noNA_MU, aes(x=age, y=diffscores)) +
  geom_point() +
  geom_smooth(method=lm , color="black", fill="grey", se=TRUE) +
  scale_y_continuous(limits = c(-5,10)) +
  theme_classic()

# x-intercept is -b0/b1
deltaMethod(MU_model, "-(Intercept)/age", level = 0.95)
```

# Additional (exploratory and supplemental) analyses

### MU Free VS Total

```{r hypotheses 3 and 4}
# Make sure dplyr is loaded
library(dplyr)

# Set cond-type to say whether it was Free-response or Total-response
condType_data <- no1shot %>%
  mutate(condType = case_when(
    condsFile %in% c("noDelayClosing", "longDelayClosing") ~ "Total",
    condsFile %in% c("noDelay", "longDelay") ~ "Free",
    TRUE ~ NA_character_
  ))

# Average over participant and condition
freeVtotal <- condType_data %>%
  group_by(participant, condType) %>%
  summarize(mean_MU = mean(meanMU, na.rm = TRUE),
            mean_StudyTime = mean(meanListTime, na.rm = TRUE),
            age = first(age),
            .groups = 'drop')

# Look at distribution of data
hist(freeVtotal$mean_MU)

# Model
freeVtotal_glmm <- glmer(mean_MU ~ condType + (1|participant),
                 data = freeVtotal, 
                    family = gaussian(link = "identity"))

# Below runs model diagnostic plots and tests
plot(density(freeVtotal$mean_MU), xlim=c(-50, 50), ylim=c(0, 0.6), 
     main='M_1 y_hat')
lines(density(predict(freeVtotal_glmm, type='response') ), col='red')

plot(freeVtotal_glmm)

residuals <- residuals(freeVtotal_glmm)
qqnorm(residuals)
qqline(residuals, col = "red")

# Use check_model from performance
library(performance)
check_model(freeVtotal_glmm)

# Compare full model with null model
MUfree_null <- glmer(mean_MU ~ 1 + (1|participant), 
                     data = freeVtotal, family = gaussian(link = "identity"))
MUfreeAov <- cbind(car::Anova(freeVtotal_glmm),
                   r.squaredGLMM(freeVtotal_glmm,MUfree_null))

anova(MUfree_null,freeVtotal_glmm)

# Get the summary
summary(freeVtotal_glmm)
MUfreeAov
```

### Effect size

```{r effect sizes}

# Get eta squared
library(effectsize)
model <- lmer(mean_StudyTime ~ age.ct * condsFile + (1 | participant), data = study_time)
eta_squared(model)

model_mu <- lmer(mean_MU ~ age.ct * condsFile + (1 | participant), data = MU_data)
eta_squared(model_mu)
```

### KS Test

This test is to see how distributed our ages are.

```{r ks test}
# Run the KS test
ks.test(MU_data$age, "punif", 
        min(MU_data$age), 
        max(MU_data$age))

# Plot the density of actual data
plot(density(MU_data$age), 
     main = "Age Distribution vs Uniform", 
     xlab = "Age", 
     ylab = "Density", 
     xlim = c(min(MU_data$age), max(MU_data$age)),
     ylim = c(0,0.6),
     lwd = 2)

# Add a horizontal line for the uniform distribution's density
abline(h = 1 / (max(MU_data$age) - min(MU_data$age)), 
       col = "red", lty = 2, lwd = 2)

legend("topright", legend = c("Observed Density", "Uniform Density"),
       col = c("black", "red"), lty = c(1,2), lwd = 2)
```

### Exploratory analyses

#### Metacognitive questions

```{r metacog questions}
# Read in data
metacog <- read.csv("data/metacog.csv",header=TRUE)

# Subset based on included participants
metacog_d <- metacog[metacog$participant %in% data$participant, ]

# Replace "Both" with NA
metacog_d <- metacog_d %>%
  mutate(across(everything(), ~ replace(.x, .x == "Both", NA)))

# Make it into a table
metaSum <- cbind(easy= table(metacog_d$easy),again =table(metacog_d$again)) %>% data.frame()

# Run the binary tests
easyTest <- binom.test(metaSum$easy[2],sum(metaSum$easy),0.5)
againTest <- binom.test(metaSum$again[2],sum(metaSum$again),0.5)

# Get the results
metaSum
easyTest
againTest
```

#### Kendall correlation

"Study time and performance: We will use a Kendall correlation to investigate whether a child’s study time is positively related to MU(total)."

```{r kendall correlation with MUtotal}

# Study time w/ MU(total)
oneshotOnly <- no1shot %>%
  filter((condsFile %in% c("noDelayClosing", "longDelayClosing")))

oneshotOnly <- oneshotOnly %>%
  group_by(participant, condsFile) %>%
  summarize(mean_MU = mean(meanMU, na.rm = TRUE),
            mean_StudyTime = mean(meanListTime, na.rm = TRUE), 
            age = first(age), 
            .groups = 'drop')

kendall_testTotal <- cor.test(oneshotOnly$mean_MU, oneshotOnly$mean_StudyTime, method = "kendall")
kendall_testTotal

# Study time w/ MU(free)
multishotOnly <- multiDataTrialSum1Trip %>%
  filter((condsFile %in% c("noDelay", "longDelay")))

multishotOnly <- multishotOnly %>%
  group_by(participant, condsFile) %>%
  summarize(mean_MU = mean(meanMU, na.rm = TRUE),
            mean_StudyTime = mean(meanListTime, na.rm = TRUE), 
            age = first(age), 
            .groups = 'drop')

kendall_test <- cor.test(multishotOnly$mean_MU, multishotOnly$mean_StudyTime, method = "kendall")
kendall_test
```

#### Regression between One-shot MU and age

```{r age and one shot mu regression}

# Make data wide
MU_wide <- pivot_wider(
  MU_data,
  id_cols = c(participant, age),
  names_from = condsFile,
  values_from = mean_MU
)

# Run simple linear regression
age_MU_lm <- lm(totalResponse ~ age, data = MU_wide)
summary(age_MU_lm)

# Plot
library(ggplot2)
ggplot(MU_wide, aes(x = age, y = totalResponse)) +
  geom_point() +
  geom_smooth(method = "lm", se = TRUE) +
  scale_y_continuous(breaks = seq(-6, 10, by = 2), limits = c(-6, 10)) +
  scale_x_continuous(breaks = seq(4.5, 7.0, by = 0.5), limits = c(4.5, 7.0)) +
  labs(
    x = "Age",
    y = "MU in One-shot"
  ) +
  theme_minimal() +
  theme(
    panel.grid = element_blank(),
    axis.line = element_line(),
    axis.ticks = element_line(),
    axis.text = element_text(size = 16),   # tick labels bigger
    axis.title = element_text(size = 18)   # axis labels bigger
  )
```

#### Regression between MU in One-shot and MU in Long-delay

```{r mu ratio}

# Run sumple regression
MU_lm <- lm(longDelay ~ totalResponse, data = MU_wide)
summary(MU_lm)

# Get r
r <- cor(MU_wide$longDelay, MU_wide$totalResponse)
r

# plot
library(ggplot2)
ggplot(MU_wide, aes(x = totalResponse, y = longDelay)) +
  geom_point() +
  geom_smooth(method = "lm", se = TRUE) +
    scale_y_continuous(breaks = seq(-2,8,by = 2), limits = c(-2, 8)) +
    scale_x_continuous(breaks = seq(-2,8, by = 2), limits = c(-2,8)) +
  labs(
    x = "MU in One-shot",
    y = "MU in Long-delay"
  ) +
  theme_minimal() +
  theme(
    panel.grid = element_blank(),   # no grid lines
    axis.line = element_line(),      # keep axes
    axis.ticks = element_line(),
        axis.text = element_text(size = 16),  
    axis.title = element_text(size = 18)
  )
```

## Supplementary materials

### Additional measures

The following describes the mean and standard deviation for the number of attempts children made on first trips in each condition, the mean and standard deviation for the amount of time children spent in the store for each condition, and the mean and standard deviation for the number of trips in each condition.

```{r additional measures}

# Number of attempts
add_measures <- data %>%
  group_by(participant, condsFile) %>%
  summarize(mean_Attempts = mean(totalClickeds, na.rm = TRUE),
            mean_shelfTime = mean(meanShelfTime, na.rm = TRUE), 
            age = first(age), 
            .groups = 'drop')

# Trips

# Load file
multiDataTrialSum <- read.csv("data/Experiment1_allTrips.csv", header = TRUE)

allTrips <- multiDataTrialSum %>%
  filter(!condsFile == "oneShot3.2") %>%
  filter(!condsFile == "oneShotClosing")

# Rename Closing trials as Total-response
allTrips <- allTrips %>%
  mutate(condsFile = case_when(
    condsFile %in% c("noDelayClosing", "longDelayClosing") ~ "totalResponse",
    TRUE ~ condsFile  # Keep the original value for all other cases
  ))

trips <- allTrips %>%
  group_by(participant, condsFile) %>%
  summarize(meanTrips = mean(nTrip, na.rm = TRUE),
            age = first(age),
            .groups = 'drop')

# Get N, change condition as needed
add_measures %>%
  filter(condsFile == "totalResponse", !is.na(mean_Attempts)) %>%
  summarise(n_unique = n_distinct(participant))

# Mean and standard deviation for each
# attempts
mean(add_measures$mean_Attempts[add_measures$condsFile == "noDelay"])
sd(add_measures$mean_Attempts[add_measures$condsFile == "noDelay"])

mean(add_measures$mean_Attempts[add_measures$condsFile == "longDelay"])
sd(add_measures$mean_Attempts[add_measures$condsFile == "longDelay"])

mean(add_measures$mean_Attempts[add_measures$condsFile == "totalResponse"])
sd(add_measures$mean_Attempts[add_measures$condsFile == "totalResponse"])

# shelf time
mean(add_measures$mean_shelfTime[add_measures$condsFile == "noDelay"])
sd(add_measures$mean_shelfTime[add_measures$condsFile == "noDelay"])

mean(add_measures$mean_shelfTime[add_measures$condsFile == "longDelay"])
sd(add_measures$mean_shelfTime[add_measures$condsFile == "longDelay"])

mean(add_measures$mean_shelfTime[add_measures$condsFile == "totalResponse"])
sd(add_measures$mean_shelfTime[add_measures$condsFile == "totalResponse"])

# trips
mean(trips$meanTrips[trips$condsFile == "noDelay"])
sd(trips$meanTrips[trips$condsFile == "noDelay"])

mean(trips$meanTrips[trips$condsFile == "longDelay"])
sd(trips$meanTrips[trips$condsFile == "longDelay"])

mean(trips$meanTrips[trips$condsFile == "totalResponse"])
sd(trips$meanTrips[trips$condsFile == "totalResponse"])
```

### Old One-shot info

```{r old one shot}
# Rename Closing trials as Total-response
multiDataTrialSum <- multiDataTrialSum %>%
  mutate(condsFile = case_when(
    condsFile %in% c("noDelayClosing", "longDelayClosing") ~ "One_Shot",
    TRUE ~ condsFile  # Keep the original value for all other cases
  ))

# Needs to be a factor to rename
multiDataTrialSum$condsFile <- as.factor(multiDataTrialSum$condsFile)

# Rename
levels(multiDataTrialSum$condsFile)[levels(multiDataTrialSum$condsFile) == "oneShot3.2"] <- "Old_One_Shot"
levels(multiDataTrialSum$condsFile)[levels(multiDataTrialSum$condsFile) == "oneShotClosing"] <- "Old_One_Shot_closing"

# MU
# Group by participant and conditions
MU_suppMaterials <- multiDataTrialSum %>%
     group_by(participant, condsFile) %>%
     summarize(mean_MU = mean(meanMU, na.rm = TRUE),
               age = first(age),
               .groups = 'drop')

# Get table of summary stats
MU_suppMaterials %>%
  group_by(condsFile) %>%
  summarise(
    Mean = mean(mean_MU, na.rm = TRUE),
    SD = sd(mean_MU, na.rm = TRUE),
    Min = min(mean_MU, na.rm = TRUE),
    Max = max(mean_MU, na.rm = TRUE),
    age = first(age),
    .groups = "drop"
  )

# Study time
# Group by participant and condition
ST_suppMaterials <- multiDataTrialSum %>%
     group_by(participant, condsFile) %>%
     summarize(mean_ST = mean(meanListTime, na.rm = TRUE), 
               age = first(age),
               .groups = 'drop')

# Get table of summary stats
ST_suppMaterials %>%
  group_by(condsFile) %>%
  summarise(
    Mean = mean(mean_ST, na.rm = TRUE),
    SD = sd(mean_ST, na.rm = TRUE),
    Min = min(mean_ST, na.rm = TRUE),
    Max = max(mean_ST, na.rm = TRUE),
    .groups = "drop"
  )

# Remove total-response trials
noTR <- MU_suppMaterials %>%
  filter(!condsFile == "Old_One_Shot_closing") %>%
  filter(!condsFile == "One_Shot")

# Center age
noTR$age.ct <- noTR$age - mean(noTR$age)

# Model for MU
MU_Old_oneShot <- glmer(mean_MU ~ condsFile + + age.ct + age.ct*condsFile +
                          (1|participant), 
                    data = noTR, 
                    family = gaussian(link = "identity"))

summary(MU_Old_oneShot)
MU_null <- glmer(mean_MU ~ 1 + (1|participant), 
                     data = noTR, family = gaussian(link = "identity"))
MUAov <- cbind(car::Anova(MU_Old_oneShot),
                   r.squaredGLMM(MU_Old_oneShot,MU_null))

# Effect size MU
library(effectsize)
model <- lmer(mean_MU  ~ condsFile + (1 | participant), data = noTR)
eta_squared(model)

model <- lmer(mean_MU  ~ age.ct + (1 | participant), data = noTR)
eta_squared(model)

model <- lmer(mean_MU  ~ age.ct*condsFile + (1 | participant), data = noTR)
eta_squared(model)

# Model for Study time
# Remove total-response trials
noTR_ST <- ST_suppMaterials %>%
  filter(!condsFile == "Old_One_Shot_closing") %>%
  filter(!condsFile == "One_Shot")

noTR_ST$age.ct <- noTR_ST$age - mean(noTR_ST$age)

ST_Old_oneShot <- glmer(mean_ST ~ condsFile + age.ct + age.ct*condsFile + 
                          (1|participant), 
                         data = noTR_ST, 
                         family = inverse.gaussian(link = "identity"), nAGQ = 0)

summary(ST_Old_oneShot)
ST_null <- lmer(mean_ST ~ 1 + (1|participant), 
                     data = noTR_ST)
STAov <- cbind(car::Anova(ST_Old_oneShot),
                   r.squaredGLMM(ST_Old_oneShot,ST_null))

# Effect sizes
model <- lmer(mean_ST  ~ condsFile + (1 | participant), data = noTR_ST)
eta_squared(model)

model <- lmer(mean_ST  ~ age.ct + (1 | participant), data = noTR_ST)
eta_squared(model)

model <- lmer(mean_ST  ~ age.ct*condsFile + (1 | participant), data = noTR_ST)
eta_squared(model)

## Free VS Total response
# Set cond-type to say whether it was Free-response or Total-response
condType_data_supp <- multiDataTrialSum %>%
  mutate(condType = case_when(
    condsFile %in% c("One_Shot", "Old_One_Shot_closing") ~ "Total",
    condsFile %in% c("noDelay", "longDelay", "Old_One_Shot") ~ "Free",
    TRUE ~ NA_character_
  ))

# Average over participant and condition
freeVtotal_supp <- condType_data_supp %>%
  group_by(participant, condType) %>%
  summarize(mean_MU = mean(meanMU, na.rm = TRUE),
            mean_StudyTime = mean(meanListTime, na.rm = TRUE),
            age = first(age),
            .groups = 'drop')

# Model
freeVtotal_glm_supp <- glmer(mean_MU ~ condType + (1|participant),
                 data = freeVtotal_supp, 
                    family = gaussian(link = "identity"))

MUsupp_null <- glmer(mean_MU ~ 1 + (1|participant), 
                     data = freeVtotal_supp, family = gaussian(link = "identity"))
MUfreeAov <- cbind(car::Anova(freeVtotal_glm_supp),
                   r.squaredGLMM(freeVtotal_glm_supp,MUsupp_null))

# Effect size
model <- lmer(mean_MU  ~ condType + (1 | participant), data = freeVtotal_supp)
eta_squared(model)

# Get mean of total-response no-delay and long-delay to compare
mean(no1shot$meanMU[no1shot$condsFile == "noDelayClosing"])
sd(no1shot$meanMU[no1shot$condsFile == "noDelayClosing"])

mean(no1shot$meanMU[no1shot$condsFile == "longDelayClosing"])
sd(no1shot$meanMU[no1shot$condsFile == "longDelayClosing"])


# Model
freeVtotal_st_supp <- lmer(mean_StudyTime ~ condType + (1|participant),
                 data = freeVtotal_supp)

STsupp_null <- lmer(mean_StudyTime ~ 1 + (1|participant), 
                     data = freeVtotal_supp)
STAov <- cbind(car::Anova(freeVtotal_st_supp),
                   r.squaredGLMM(freeVtotal_st_supp,STsupp_null))

```

#### Screen use

```{r screen use}

# Group by participant 
participant_data <- data %>%
  group_by(participant) %>%
  slice(1) %>%
    ungroup()

# Organize into numeric data
participant_data <- participant_data %>%
  mutate(screen_use_numeric = case_when(
    screen_use_hour == "0" ~ 0,
    screen_use_hour == "0-1 hour" ~ 1,
    screen_use_hour == "1-2 hours" ~ 2,
    screen_use_hour == "2-3 hours" ~ 3,
    TRUE ~ NA_real_
  ))

# Get mean and SD
mean(participant_data$screen_use_numeric, na.rm = T)
sd(participant_data$screen_use_numeric, na.rm = T)

```

#### All trips

```{r all trips process}
# Get mean and sd for each condition
mean(data$meanMU[data$condsFile == "noDelay"])
sd(data$meanMU[data$condsFile == "noDelay"])

mean(data$meanMU[data$condsFile == "longDelay"])
sd(data$meanMU[data$condsFile == "longDelay"])

mean(data$meanMU[data$condsFile == "totalResponse"])
sd(data$meanMU[data$condsFile == "totalResponse"])

# study time
mean(data$meanListTime[data$condsFile == "noDelay"])
sd(data$meanListTime[data$condsFile == "noDelay"])

mean(data$meanListTime[data$condsFile == "longDelay"])
sd(data$meanListTime[data$condsFile == "longDelay"])

mean(data$meanListTime[data$condsFile == "totalResponse"])
sd(data$meanListTime[data$condsFile == "totalResponse"])
```

##### Study time

```{r all trips study time}
# Average over all trials for each condition, for each child, as per preregistration
study_time <- data %>%
  group_by(participant, condsFile) %>%
  summarize(mean_MU = mean(meanMU, na.rm = TRUE),
            mean_StudyTime = mean(meanListTime, na.rm = TRUE), 
            age = first(age), 
            .groups = 'drop')

# Center age
study_time$age.ct <- study_time$age - mean(study_time$age)

# make sure condition is a factor
study_time$condsFile <- as.factor(study_time$condsFile)

# Run model
studyTime_all <- glmer(mean_StudyTime ~ condsFile + age.ct + age.ct*condsFile + (1|participant), 
                         data = study_time, 
                         family = inverse.gaussian(link = "identity"), nAGQ = 0)

mixConTime_GLMM_null <- glmer(mean_StudyTime ~ 1 + (1|participant), 
                              data = study_time, 
                              family = inverse.gaussian(link = "identity"), nAGQ = 0)
mixTimeConAov <- cbind(car::Anova(studyTime_all),
                       r.squaredGLMM(studyTime_all,mixConTime_GLMM_null)) 

# Effect size
library(effectsize)
model <- lmer(mean_StudyTime ~ condsFile + (1|participant), 
                         data = study_time)
eta_squared(model)

model <- lmer(mean_StudyTime ~ age.ct + (1|participant), 
                         data = study_time)
eta_squared(model)

model <- lmer(mean_StudyTime ~ age.ct*condsFile + (1|participant), 
                         data = study_time)
eta_squared(model)
```

##### MU

```{r all trips mu}
# Average over participant and condition
MU_data <- data %>%
  group_by(participant, condsFile) %>%
  summarize(mean_MU = mean(meanMU, na.rm = TRUE), 
            age = first(age), 
            .groups = 'drop')

# Center age
MU_data$age.ct <- MU_data$age - mean(MU_data$age)

# Run the model
MU_all <- glmer(mean_MU ~ condsFile + age.ct + age.ct*condsFile + (1|participant), 
                    data = MU_data, 
                    family = gaussian(link = "identity"))

# Get the p value, and R squared
MUfree_null <- glmer(mean_MU ~ 1 + (1|participant), 
                     data = MU_data, family = gaussian(link = "identity"))
MUfreeAov <- cbind(car::Anova(MU_all),
                   r.squaredGLMM(MU_all,MUfree_null))

# Effect size
model <- lmer(mean_MU ~ condsFile + (1|participant), 
                         data = MU_data)
eta_squared(model)

model <- lmer(mean_MU ~ age.ct + (1|participant), 
                         data = MU_data)
eta_squared(model)

model <- lmer(mean_MU ~ age.ct*condsFile + (1|participant), 
                         data = MU_data)
eta_squared(model)
```

### Comparisons with Liang et al.

Trips

```{r trips}

# Get mean and SD
mean(multiDataTrialSum$nTrip[multiDataTrialSum$condsFile == "noDelay"],)
mean(multiDataTrialSum$nTrip[multiDataTrialSum$condsFile == "longDelay"],)
sd(multiDataTrialSum$nTrip[multiDataTrialSum$condsFile == "noDelay"],)
sd(multiDataTrialSum$nTrip[multiDataTrialSum$condsFile == "longDelay"],)
```

Streak correct

```{r streak correct}
# Average over participant and condition
Streak_data <- data %>%
  group_by(participant, condsFile) %>%
  summarize(mean_Streak = mean(meanCorBefInc, na.rm = TRUE), 
            .groups = 'drop')

# Get mean and SD
mean(Streak_data$mean_Streak[Streak_data$condsFile == "noDelay"],)
mean(Streak_data$mean_Streak[Streak_data$condsFile == "longDelay"],)
sd(Streak_data$mean_Streak[Streak_data$condsFile == "noDelay"],)
sd(Streak_data$mean_Streak[Streak_data$condsFile == "longDelay"],)

```

### Random effects comparisons

Study time:

```{r random effect comparisons}
# Following Barr et al (2013) we start with the maximal model

# Center age
data$age.ct <- data$age - mean(data$age)

# make sure condition is a factor
data$condsFile <- as.factor(data$condsFile)

# Maximal model
studytime_m1 <- glmer(meanListTime ~ condsFile + age.ct + age.ct*condsFile + (1 + condsFile|participant) + (1|trial), 
                       data = data, 
                       family = inverse.gaussian(link = "identity"), nAGQ = 0)

# Model without correlations between slopes and intercept
studytime_m2 <- glmer(meanListTime ~ condsFile + age.ct + age.ct*condsFile + (1|participant) + (0 + condsFile|participant) + (1|trial), 
                        data = data, 
                        family = inverse.gaussian(link = "identity"), nAGQ = 0)

# Using repca, assess dimensionality
rePCA(studytime_m2)

# Compare with model with one less step complexity
studytime_m3 <- glmer(meanListTime ~ condsFile + age.ct + age.ct*condsFile + 
                        (0 + condsFile|participant) + (1|trial), 
                        data = data, 
                        family = inverse.gaussian(link = "identity"), nAGQ = 0)

# Compare
anova(studytime_m2, studytime_m3)

```

Memory Use:

```{r random effects memory use}
# Reference level should be One-shot, sum contrasts
data$condsFile <- factor(
  data$condsFile,
  levels = c("longDelay", "noDelay", "totalResponse")
)
contrasts(data$condsFile) <- contr.sum(3)

# Maximal model
MU_m1 <- lmer(meanMU ~ condsFile + age.ct + age.ct*condsFile + (1 + condsFile|participant) + (1|trial), 
                data = data)

# Model without correlations between slopes and intercept
MU_m2 <- lmer(meanMU ~ condsFile + age.ct + age.ct*condsFile + (1|participant) + (0 + condsFile|participant) + (1|trial), 
                data = data)

# Model with slopes and no intercept
MU_m3 <- lmer(meanMU ~ condsFile + age.ct + age.ct*condsFile + (0 + condsFile|participant) + (1|trial), 
                data = data)

# Only participant and trial intercepts
MU_m4 <- lmer(meanMU ~ condsFile + + age.ct + age.ct*condsFile + 
                (1|participant) + (1|trial), 
                data = data)

# Only slopes
MU_m5 <- lmer(meanMU ~ condsFile + age.ct + age.ct*condsFile + (1 + condsFile|participant), 
                data = data)

# Only participant intercept
MU_m6 <- lmer(meanMU ~ condsFile + age.ct + age.ct*condsFile + (1|participant), 
                data = data)
```

# Plots

##### Figure 6, Study time and Memory Use across conditions

```{r fig 6}
# Rename values in the 'condsFile' column
study_time$condsFile <- as.character(study_time$condsFile)
study_time$condsFile[study_time$condsFile == "noDelay"] <- "No-delay"
study_time$condsFile[study_time$condsFile == "longDelay"] <- "Long-delay"
study_time$condsFile[study_time$condsFile == "totalResponse"] <- "One-shot"

# 95% CI function
ci95 <- function(x) {
  x <- x[!is.na(x)]
  m  <- mean(x)
  se <- sd(x) / sqrt(length(x))
  # t-critical value for 95 % CI
  tcrit <- qt(0.975, df = length(x) - 1)
  c(lower = m - tcrit * se,
    upper = m + tcrit * se)
}

par(mfrow = c(1, 2))

# study time ------------
# Calculate means
means <- tapply(study_time$mean_StudyTime, study_time$condsFile, mean)

# Define the x-axis levels (to match the ggplot2 ordering)
conds_levels <- c("No-delay", "Long-delay", "One-shot")
x_positions <- 1:length(conds_levels)

# Create an empty plot
plot(
  x_positions, means[conds_levels], 
  type = "n", xaxt = "n", yaxt = "n", ylim = c(0, 30.0), xlim = c(0.5, 3.5),
  xlab = "", ylab = "Mean Study Time (seconds)", 
  main = "",
  cex.lab = 1.5,
  cex.axis = 1.5,
  cex.main = 1.1
)

axis(2, at = seq(0, 28, by = 4), cex.axis = 1.2)

participants <- unique(study_time$participant)

for (p in participants) {
  this_participant <- study_time[study_time$participant == p, ]
  if (nrow(this_participant) == 3) {
    # Get the x positions for this participant’s conditions
    x_vals <- match(this_participant$condsFile, conds_levels)
    y_vals <- this_participant$mean_StudyTime
    lines(x_vals, y_vals, col = adjustcolor("#009E73", alpha.f = 0.3), lwd = 1)
  }
}

# Add x-axis labels normally
axis(1, at = x_positions, labels = conds_levels, cex.axis = 1.2)

# Add points for each participant
for (i in 1:length(conds_levels)) {
  condition_data <- study_time[study_time$condsFile == conds_levels[i], ]
  points(rep(x_positions[i], nrow(condition_data)), condition_data$mean_StudyTime, 
         pch = 1, col = "#0072B2")
}

# Add points for the means
points(x_positions, means[conds_levels], pch = 10, col = "black")

# Add a solid line connecting the means
#lines(x_positions, means[conds_levels], col = "black", lwd = 2)

# Add horizontal segments at the means (optional, similar to ggplot2's stat_summary)
segments(
  x_positions - 0.1, means[conds_levels], 
  x_positions + 0.1, means[conds_levels],
  col = "black", lwd = 3.0
)

# Add mean labels for each condition
#text(x_positions, means[conds_levels] + 3, 
#     labels = round(means[conds_levels], 2), cex = 1.5, col = "black")

# Get means again, just to be sure
means <- tapply(study_time$mean_StudyTime, study_time$condsFile, mean)

# compute CIs for study time
cis <- tapply(study_time$mean_StudyTime,
              study_time$condsFile,
              ci95)

# pull them out in the plotting order
lower_bounds <- sapply(cis[conds_levels], function(x) x["lower"])
upper_bounds <- sapply(cis[conds_levels], function(x) x["upper"])

# Add vertical error bars using arrows()
for (i in 1:length(x_positions)) {
  arrows(
    x0 = x_positions[i], y0 = lower_bounds[i], 
    x1 = x_positions[i], y1 = upper_bounds[i], 
    length = 0.1, angle = 90, code = 3, col = "#D55E00", lwd = 3.5
  )
}



# MU ------------
MU_data$condsFile <- as.character(MU_data$condsFile)
MU_data$condsFile[MU_data$condsFile == "noDelay"] <- "No-delay"
MU_data$condsFile[MU_data$condsFile == "longDelay"] <- "Long-delay"
MU_data$condsFile[MU_data$condsFile == "totalResponse"] <- "One-shot"

# Calculate means and standard errors
means <- tapply(MU_data$mean_MU, MU_data$condsFile, mean)

# Calculate standard deviations and sample sizes for each condition
sds <- tapply(MU_data$mean_MU, MU_data$condsFile, sd)
n_per_condition <- tapply(MU_data$mean_MU, MU_data$condsFile, length)

# Calculate standard errors
se <- sds / sqrt(n_per_condition)

# Define the x-axis levels (to match the ggplot2 ordering)
conds_levels <- c("No-delay", "Long-delay", "One-shot")
x_positions <- 1:length(conds_levels)

# Create an empty plot
plot(
  x_positions, means[conds_levels], 
  type = "n", xaxt = "n", yaxt = "n", ylim = c(-5, 10.0), xlim = c(0.5, 3.5),
  xlab = "", ylab = "Mean Memory Usage (items)", 
  main = "",
  cex.lab = 1.5,
  cex.axis = 1.5,
  cex.main = 1.1
)

axis(2, at = seq(-5, 10, by = 1), labels = ifelse(seq(-5, 10, by = 1) %% 2 == 0, seq(-5, 10, by = 1), ""), cex.axis = 1.2)

participants <- unique(MU_data$participant)

for (p in participants) {
  this_participant <- MU_data[MU_data$participant == p, ]
  if (nrow(this_participant) == 3) {
    # Get the x positions for this participant’s conditions
    x_vals <- match(this_participant$condsFile, conds_levels)
    y_vals <- this_participant$mean_MU
    lines(x_vals, y_vals, col = adjustcolor("#009E73", alpha.f = 0.3), lwd = 1)
  }
}

# Add x-axis labels normally
axis(1, at = x_positions, labels = conds_levels, cex.axis = 1.2)

# Add points for each participant
for (i in 1:length(conds_levels)) {
  condition_data <- MU_data[MU_data$condsFile == conds_levels[i], ]
  points(rep(x_positions[i], nrow(condition_data)), condition_data$mean_MU, 
         pch = 1, col = "#0072B2")
}

# Add points for the means
points(x_positions, means[conds_levels], pch = 10, col = "black")

# Add a solid line connecting the means
#lines(x_positions, means[conds_levels], col = "black", lwd = 2)

# Add horizontal segments at the means (optional, similar to ggplot2's stat_summary)
segments(
  x_positions - 0.1, means[conds_levels], 
  x_positions + 0.1, means[conds_levels],
  col = "black", lwd = 3.0
)

# Add mean labels for each condition
#text(x_positions, means[conds_levels] + 2, 
#     labels = round(means[conds_levels], 2), cex = 1.5, col = "black")

# Get means again, just to be sure
means <- tapply(MU_data$mean_MU, MU_data$condsFile, mean)

# compute CIs for study time
cis <- tapply(MU_data$mean_MU,
              MU_data$condsFile,
              ci95)

# pull them out in the plotting order
lower_bounds <- sapply(cis[conds_levels], function(x) x["lower"])
upper_bounds <- sapply(cis[conds_levels], function(x) x["upper"])

# Add vertical error bars using arrows()
for (i in 1:length(x_positions)) {
  arrows(
    x0 = x_positions[i], y0 = lower_bounds[i], 
    x1 = x_positions[i], y1 = upper_bounds[i], 
    length = 0.1, angle = 90, code = 3, col = "#D55E00", lwd = 3.5
  )
}
```

##### Figure 7, Age interaction

```{r fig 7}
par(mfrow = c(1, 2))

# study time --------------
# Define levels and colors
conds_levels <- c("No-delay", "Long-delay", "One-shot")
colors <- c("#0072B2", "#D55E00", "#009E73")

# Create empty plot
plot(
  NA, xlim = c(4.5,7.0), ylim = c(0, 15),
  xlab = "Age", ylab = "Study time (seconds)",
  cex.lab = 1.6, cex.axis = 1.5, yaxt = "n",
)

axis(2, at = seq(0, 15, by = 3), cex.axis = 1.2)

for (i in seq_along(conds_levels)) {
  # Filter data
  condition_data <- study_time[study_time$condsFile == conds_levels[i], ]
  
  # Scatter points
  #points(condition_data$age, condition_data$mean_StudyTime,
  #       col = adjustcolor(colors[i], alpha.f = 0.4), pch = 16)
  
  # Fit linear model
  lm_fit <- lm(mean_StudyTime ~ age, data = condition_data)
  
  # Create a sequence of ages for smooth line
  new_ages <- seq(min(condition_data$age), max(condition_data$age), length.out = 100)
  
  # Predict with confidence intervals
  pred <- predict(lm_fit, newdata = data.frame(age = new_ages), interval = "confidence")
  
  # Draw CI as a polygon
  polygon(
    c(new_ages, rev(new_ages)),
    c(pred[,"lwr"], rev(pred[,"upr"])),
    col = adjustcolor(colors[i], alpha.f = 0.2), border = NA
  )
  
  # Draw regression line
  lines(new_ages, pred[,"fit"], col = colors[i], lwd = 2)
}

# Add legend
#legend("topright", legend = conds_levels, col = colors, lty = 1, lwd = 2, pch = 16)

# MU ##########
conds_levels <- c("No-delay", "Long-delay", "One-shot")
colors <- c("#0072B2", "#D55E00", "#009E73")

# Create empty plot
plot(
  NA, xlim = c(4.5,7.0), ylim = c(-2,7),
  xlab = "Age", ylab = "Memory Usage (items)", 
  cex.lab = 1.6, cex.axis = 1.5, yaxt = "n",
)

axis(2, at = seq(-2, 7, by = 2), cex.axis = 1.2)

for (i in seq_along(conds_levels)) {
  # Filter data
  condition_data <- MU_data[MU_data$condsFile == conds_levels[i], ]
  
  # Scatter points
  #points(condition_data$age, condition_data$mean_StudyTime,
  #       col = adjustcolor(colors[i], alpha.f = 0.4), pch = 16)
  
  # Fit linear model
  lm_fit <- lm(mean_MU ~ age, data = condition_data)
  
  # Create a sequence of ages for smooth line
  new_ages <- seq(min(condition_data$age), max(condition_data$age), length.out = 100)
  
  # Predict with confidence intervals
  pred <- predict(lm_fit, newdata = data.frame(age = new_ages), interval = "confidence")
  
  # Draw CI as a polygon
  polygon(
    c(new_ages, rev(new_ages)),
    c(pred[,"lwr"], rev(pred[,"upr"])),
    col = adjustcolor(colors[i], alpha.f = 0.2), border = NA
  )
  
  # Draw regression line
  lines(new_ages, pred[,"fit"], col = colors[i], lwd = 2)
}

# Add legend
#legend("topright", legend = conds_levels, col = colors, lty = 1, lwd = 2, pch = 16)

```

Difference score plots:

```{r age of emergence difference score plot}

# Plot
pMU <- ggplot(noNA_MU, aes(x=age, y=diffscores)) +
  geom_point() +
  geom_smooth(method=lm , color="black", fill="grey", se=TRUE) +
  theme_classic()

pStudytime <- ggplot(noNA_ST, aes(x=age, y=diffscores)) +
  geom_point() +
  geom_smooth(method=lm , color="black", fill="grey", se=TRUE) +
  theme_classic()
```
